\documentclass[10pt,twocolumn,a4paper]{article}
\usepackage{fontspec}
\usepackage[top=1cm,bottom=1.5cm,left=1cm,right=1cm]{geometry}
\usepackage[czech,english]{babel}
\usepackage{color}
\usepackage{graphicx}
\usepackage{ifthen}
\usepackage{calc}
\usepackage{gchords}
\usepackage{gtrcrd}
%

%\pagestyle{empty}

%\documentclass[a4paper,twocolumn,czech,10pt]{article}
%\usepackage[cp1250]{inputenc}
%\usepackage[T1]{fontenc}
%\usepackage{babel}
%\usepackage{color}
%\usepackage{graphicx}
%\usepackage{ifthen}
%\usepackage{calc}
%\usepackage{gchords}
%%
%\oddsidemargin -1cm \evensidemargin -1cm \textwidth 18cm \textheight 25.5cm \topmargin -2.3cm

%
\usepackage{fancyhdr}

\usepackage{makeidx}
\makeindex
\pagestyle{plain}

%
%------definition of font colors-----------
\definecolor{chorus}{rgb}{1,0,0}
\definecolor{bridge}{rgb}{0,0,1}
\definecolor{instr}{rgb}{.3,.3,.3}
\definecolor{tab}{rgb}{.3,.3,.3}
\definecolor{second_text}{rgb}{1,1,1}
\definecolor{second_back}{rgb}{.7,.7,.7}
%
%------definition of environments-------
\newenvironment{chorus}{\color{chorus}}{\normalcolor}
\newenvironment{bridge}{\color{bridge}}{\normalcolor}
\newenvironment{instr}{\color{instr}}{\normalcolor}
\newenvironment{gtxtab}{\color{tab}}{\normalcolor}
%
%------counter for line numbers------
%\newcounter{verscnt}[section]
%\newcommand{\vers}{\stepcounter{verscnt}%
%\makebox[0.5cm][r]{\scriptsize\theverscnt\normalsize}%
%\makebox[0.5cm]{}}
%
\newcommand{\gtxchordsize}{\footnotesize}
\setlength{\parindent}{0pt}

%------PostScript-Header für die Chord-Songs------
%\special{header=/usr/local/lib/guitartex/chord-common.ps}

\sloppy
\setlength{\unitlength}{1mm}

\newcommand{\gtxchord}[2]{\sbox{\gtxchordbox}{#1}\sbox{\textbox}{#2}%
	\ifthenelse{\lengthtest{\wd\textbox>\wd\gtxchordbox}}%
	{%
		\raisebox{2ex}[2ex][2.5ex]{\makebox[0pt][l]{\scriptsize\bf#1}}#2%
	}{%
	\raisebox{2ex}[2ex][2.5ex]{\makebox[0pt][l]{\scriptsize\bf#1}}\makebox[\wd\gtxchordbox+0.5em][l]{#2}%
	}%
}%

\newcommand{\guitartab}{%
\makebox[0cm][l]{\raisebox{12.5ex}{\footnotesize{e}}}%
\makebox[0cm][l]{\raisebox{10.5ex}{\footnotesize{B}}}%
\makebox[0cm][l]{\raisebox{8.5ex}{\footnotesize{G}}}%
\makebox[0cm][l]{\raisebox{6.5ex}{\footnotesize{D}}}%
\makebox[0cm][l]{\raisebox{4.5ex}{\footnotesize{A}}}%
\makebox[0cm][l]{\raisebox{2.5ex}{\footnotesize{E}}}%
~~
\makebox[0cm][l]{\raisebox{13ex}{\line(1,0){130}}}%
\makebox[0cm][l]{\raisebox{11ex}{\line(1,0){130}}}%
\makebox[0cm][l]{\raisebox{9ex}{\line(1,0){130}}}%
\makebox[0cm][l]{\raisebox{7ex}{\line(1,0){130}}}%
\makebox[0cm][l]{\raisebox{5ex}{\line(1,0){130}}}%
\makebox[0cm][l]{\raisebox{3ex}{\line(1,0){130}}}%
~}

\newcommand{\basstab}{%
\makebox[0cm][l]{\raisebox{8.5ex}{\footnotesize{G}}}%
\makebox[0cm][l]{\raisebox{6.5ex}{\footnotesize{D}}}%
\makebox[0cm][l]{\raisebox{4.5ex}{\footnotesize{A}}}%
\makebox[0cm][l]{\raisebox{2.5ex}{\footnotesize{E}}}%
~~
\makebox[0cm][l]{\raisebox{9ex}{\line(1,0){130}}}%
\makebox[0cm][l]{\raisebox{7ex}{\line(1,0){130}}}%
\makebox[0cm][l]{\raisebox{5ex}{\line(1,0){130}}}%
\makebox[0cm][l]{\raisebox{3ex}{\line(1,0){130}}}%
~}

\newcommand{\gtxtabs}[2]{\makebox[0cm][l]{\raisebox{#1}{#2}}}
%
%
%

% faking table of contents
\makeatletter
\renewcommand*{\tableofcontents}{%
  \begingroup
    \let\@input\@gobble
    \@starttoc{toc}%
  \endgroup
}
\makeatother
% end fake table of contents


%
%
%

%------start of document-----------
\begin{document}
\tableofcontents % this is fake, no output
\newsavebox{\gtxchordbox}
\newsavebox{\textbox}
\setcounter{page}{108}

\newpage
\addcontentsline{toc}{section}{She's Not There}
\section*{She's Not There}
\index{She's Not There}\typeout{She's Not There}\index{The Zombies!She's Not There}\textit{The Zombies}

\textit{Intro:}\\
\begin{gtxtab}
\footnotesize \verb!     (Bass notes)! \normalsize \newline
\footnotesize \verb!|----||-----------------|-----------------||! \normalsize \newline
\footnotesize \verb!|--2-||-----2---0-4-2---|-----2---0-4-2---||! \normalsize \newline
\footnotesize \verb!|----||-0-----0---------|-0-----0---------||! \normalsize \newline
\footnotesize \verb!|----||-----------------|-----------------||! \normalsize \newline
\end{gtxtab}
~\\
\gtxchord{Am}{Well~no~one~}\gtxchord{D}{told~me~a}\gtxchord{Am7}{bout~}\gtxchord{D}{her~}\\
\gtxchord{Am}{The~}\gtxchord{F}{way~she~}\gtxchord{Am}{lied~}\gtxchord{D}{~}\\
\gtxchord{Am7}{Well~no~one~}\gtxchord{D}{told~me~a}\gtxchord{Am7}{bout~}\gtxchord{D}{her~}\\
\gtxchord{Am}{How~many~}\gtxchord{F}{people~}\gtxchord{A}{cried~}\\
~\\
\textit{Chorus:}\\
~\\
\gtxchord{}{Well~it's~too~}\gtxchord{D}{late~to~}\gtxchord{Dm}{say~you're~}\gtxchord{Am}{sorry~}\\
\gtxchord{}{How~would~I~}\gtxchord{Em}{know,~why~should~I~}\gtxchord{Am}{care?~}\\
\gtxchord{}{Please~don't~}\gtxchord{D}{bother~}\gtxchord{Dm}{trying~to~}\gtxchord{C}{find~her~}\\
\gtxchord{}{She's~not~}\gtxchord{E7}{there~}\\
~\\
\gtxchord{}{Well~let~me~tell~you~'bout~the~}\gtxchord{Am}{way~she~looked~}\\
\gtxchord{D}{The~way~she~}\gtxchord{Am}{acted,~the~}\gtxchord{F}{color~of~her~}\gtxchord{Am}{hair}\gtxchord{D}{~}\\
\gtxchord{}{Her~voice~was~}\gtxchord{Am}{soft~and~good,~}\gtxchord{F}{~her~eyes~were~}\gtxchord{Am}{clear~and~bright~}\\
\gtxchord{D}{But~she's~not~there~}\\
~\\
Well no one told me about her \\
What could I do \\
Well no one told me about her \\
Though they all knew \\
~\\
\textit{Chorus:}\\
\textit{Solo:}\\ \\
\gtxchord{Am}{~}\gtxchord{D}{~(7x)~~~~}\gtxchord{A}{~}\gtxchord{A7}{~}\\
\textit{Chorus:}\\
~\\

\addcontentsline{toc}{section}{Who By Fire}
\section*{Who By Fire}
\index{Who By Fire}\typeout{Who By Fire}\index{Leonard Cohen!Who By Fire}\textit{Leonard Cohen}

\textit{intro:}\\ \\
\gtxchord{Am/E}{~}\gtxchord{Am/F}{~}\gtxchord{E(7)}{~}\gtxchord{E(7)}{~}\\
~\\
\textit{1.}\\
\gtxchord{}{And~}\gtxchord{Am}{who~}\gtxchord{G}{by~}\gtxchord{Am}{fire,~}\gtxchord{Am}{who~}\gtxchord{G}{by~}\gtxchord{Am}{water,~}\\
\gtxchord{C/E}{who~}\gtxchord{G/D}{in~the~}\gtxchord{C/E}{sunshine,~}\gtxchord{C/E}{who~}\gtxchord{G/D}{in~the~}\gtxchord{C/E}{night~time,~}\\
\gtxchord{Am}{who~}\gtxchord{G}{by~}\gtxchord{Am}{high~ordeal,~}\gtxchord{Am}{who~}\gtxchord{G}{by~}\gtxchord{Am}{common~trial,~}\\
\gtxchord{C/E}{who~in~your~}\gtxchord{G/D}{merry~merry~}\gtxchord{C/E}{month~of~may,~}\\
\gtxchord{C/E}{who~by~}\gtxchord{G/D}{very~}\gtxchord{C/E}{slow~decay,~}\\
\gtxchord{}{and~}\gtxchord{Am/E}{who~shall~I~sa}\gtxchord{Am/F}{y~is~}\gtxchord{E/B}{calling?~}\gtxchord{E/B}{~}\\
~\\
\textit{2.}\\
And~who~in~her~lonely~slip,~who~by~barbiturate,~\\
who~in~these~realms~of~love,~who~by~something~blunt,~\\
and~who~by~avalanche,~who~by~powder,~\\
who~for~his~greed,~who~for~his~hunger,~\\
and~who~shall~I~say~is~calling?~\\
~\\
\textit{3.}\\
And~who~by~brave~assent,~who~by~accident,~\\
who~in~solitude,~who~in~this~mirror,~\\
who~by~his~lady's~command,~who~by~his~own~hand,~\\
who~in~mortal~chains,~who~in~power,~\\
and~who~shall~I~say~is~calling?~~\\
~\\

\addcontentsline{toc}{section}{I'll Get You}
\section*{I'll Get You}
\index{I'll Get You}\typeout{I'll Get You}\index{The Beatles!I'll Get You}\textit{The Beatles}


\textit{1.}\\
\gtxchord{}{Oh~}\gtxchord{D$\flat$}{yeah,~~oh~y}\gtxchord{A$\flat$}{eah,~oh~}\gtxchord{D$\flat$}{yeah,~oh~}\gtxchord{A$\flat$}{yeah.}\\
\gtxchord{}{I}\gtxchord{D$\flat$}{magine~I'm~in~love~with~you~it's~}\gtxchord{G$\flat$}{easy~'cause~I~}\gtxchord{A$\flat$7}{know;}\\
\gtxchord{}{I've~i}\gtxchord{D$\flat$}{magined~I'm~in~}\gtxchord{Bm}{love~with~you}\\
\gtxchord{G$\flat$}{many,~many,~many~times~be}\gtxchord{A$\flat$}{fore.}\\
\gtxchord{}{It's~not~}\gtxchord{D$\flat$}{like~me~to~pre}\gtxchord{A$\flat$m}{tend,~but~I'll~}\gtxchord{D$\flat$}{get~you.}\\
\gtxchord{}{I'll~get~you~in~the~}\gtxchord{B$\flat$m}{end;}\\
\gtxchord{}{Yes,~I~}\gtxchord{G$\flat$}{will,~I'll~get~you~in~the~}\gtxchord{A$\flat$7}{end.}\\


\textit{2.}\\
Oh~yeah,~~oh~yeah,~oh~yeah,~oh~yeah.\\
I~think~about~you~night~and~day.\\
I~need~you~and~it's~true;\\
When~I~think~about~you~I~can~say\\
I'm~never,~never,~never~never~blue.\\
So~I'm~telling~you,~my~friend,\\
That~I'll~get~you,~I'll~get~you~in~the~end;\\
Yes,~I~will,~I'll~get~you~in~the~end.\\




\textit{bridge:}\\ \\
\gtxchord{}{Oh~}\gtxchord{D$\flat$}{yeah,~oh~}\gtxchord{Am}{yeah}\\
\gtxchord{G$\flat$}{Well,~there's~gonna~be~a~time}\\
\gtxchord{D$\flat$}{When~I'm~gonna~change~your~mind.}\\
\gtxchord{E$\flat$7}{So~you~might~as~well~resign~your}\gtxchord{A$\flat$7}{self~to~me.~Oh~yeah.}\\


\textit{1.}\\


[:~Oh~yeah,~oh~yeah~:]{~Oh~yeah.}


%
%----- New Song -----
\newpage

\addcontentsline{toc}{section}{All For Love}
\section*{All For Love}
\index{All For Love}\typeout{All For Love}\index{Bryan Adams, Sting \& Rod Stewart!All For Love}\textit{Bryan Adams, Sting \& Rod Stewart}\\


\textit{Verse 1:}\\

\gtxchord{D}{When~it's~love}\gtxchord{Dsus4}{~you~g}\gtxchord{D}{ive,~(I'll~be~a~man~of~good~faith.)}\\
\gtxchord{D}{then~in~love}\gtxchord{Dsus4}{~you~~l}\gtxchord{D}{ive.~(I'll~make~a~stand.~I~won't~break.)}\\
\gtxchord{D/F$\sharp$}{I'll~be~the~rock~you~can~build~on}\gtxchord{G}{,}\\
\gtxchord{}{be~there~when~you're~old,}\gtxchord{D/A}{}\\
\gtxchord{}{to~have~and~to~hold}\gtxchord{A}{.}\\

\textit{Verse 2:}\\
When~there's~love~inside~(I~swear~I'll~always~be~strong.)\\
then~there's~a~reason~why.(I'll~prove~to~you~we~belong.)\\
I'll~be~the~wal~that~protects~you\\
from~the~wind~and~the~rain,\\
\gtxchord{}{from~the~hurt~and~}\gtxchord{A}{pain.}\gtxchord{Asus4}{}\gtxchord{A}{}\\


\textit{Chorus:}\\

\gtxchord{D}{~~}\gtxchord{Em7}{~~}\gtxchord{D/F$\sharp$}{~~~}\gtxchord{(N.C.)}{}\\
\gtxchord{}{Let's~make~it~}\gtxchord{Em}{all~}\gtxchord{D}{for~}\gtxchord{A}{one~and~}\gtxchord{D/F$\sharp$}{all~for~}\gtxchord{G}{love.}\\
\gtxchord{Em7}{Let~the~one~you~hold~be~the~one~you~w}\gtxchord{D/A}{ant,~the~one~you~need,}\gtxchord{A}{}\\
\gtxchord{}{'cause~wh}\gtxchord{D/F$\sharp$}{en~it's~all~}\gtxchord{G}{for~}\gtxchord{Bm}{one~}\gtxchord{A}{it's~one~}\gtxchord{D/F$\sharp$}{for~all.}\gtxchord{G}{}\\
\gtxchord{}{When~there's~some}\gtxchord{Em7}{one~that~you~}\gtxchord{D/F$\sharp$}{know}\\
\gtxchord{}{then~just~}\gtxchord{G}{let~your~feelin}\gtxchord{D/A}{gs~show}\\
\gtxchord{}{and~make~it~al}\gtxchord{G}{l~fo}\gtxchord{D/F$\sharp$}{r~~on}\gtxchord{Em}{e~and~al}\gtxchord{A}{l~for~lov}\gtxchord{D}{e.}\\


\textit{Verse 3:}\\
When~it's~love~you~make~(I'll~be~the~fire~in~your~night.)\\
then~it's~love~you~take.~(I~will~defend,~I~will~fight.)\\
I'll~be~there~when~you~need~me.\\
When~honor's~at~stake,\\
this~vow~I~will~make.\\


\textit{Chorus:}\\
Then~it's~...\\


\textit{Bridge:}\\


\gtxchord{Bm}{Don't~lay~our~lov}\gtxchord{G}{e~to~rest}\\
\gtxchord{}{'cause~we~could~stan}\gtxchord{Em7}{d~up~to~}\gtxchord{D/F$\sharp$}{the~test}\gtxchord{G}{}\\
\gtxchord{A}{We~got~}\gtxchord{Bm}{everything~and~more}\gtxchord{D/F$\sharp$}{~than~we~had~plan}\gtxchord{G}{ned,}\gtxchord{Asus4}{}\\
\gtxchord{A}{more~than~the~rive}\gtxchord{Bm}{rs~that~run~the~land.}\gtxchord{D/F$\sharp$}{}\\
\gtxchord{}{We've~got~it~}\gtxchord{G}{all~in~our}\gtxchord{A}{~hands.}\\




\textit{Solo:}\\




\textit{Chorus:}\\
Now~it's~...\\


\addcontentsline{toc}{section}{Adeste Fideles}
\section*{Adeste Fideles}
\index{Adeste Fideles}\typeout{Adeste Fideles}

\gtxchord{}{A}\gtxchord{F}{deste~fid}\gtxchord{C}{eles,~}\gtxchord{F}{laeti~triu}\gtxchord{B$\flat$}{m~-}\gtxchord{F}{phan}\gtxchord{C}{tes,}\\
\gtxchord{}{ve~}\gtxchord{G7}{-nite,~ve}\gtxchord{C}{-ni-te~in~}\gtxchord{C}{Be--}\gtxchord{G}{--tle}\gtxchord{C}{-hem.}\\
\gtxchord{F}{Natum~vi-}\gtxchord{Gm}{de-}\gtxchord{F}{te~}\gtxchord{C}{Regem~}\gtxchord{Dm}{ange-}\gtxchord{C}{lorum.}\\
\gtxchord{}{Ve-}\gtxchord{F}{nite~a-do-}\gtxchord{F}{remus,~ve-}\gtxchord{F}{nite~a-}\gtxchord{B$\flat$}{do-}\gtxchord{B$\flat$}{re-m}\gtxchord{C}{us,}\\
\gtxchord{}{ve-}\gtxchord{B$\flat$}{nite~a-do-}\gtxchord{C}{re--}\gtxchord{Dm}{mu-s~~~}\gtxchord{F}{Do---}\gtxchord{C}{mi-nu}\gtxchord{F}{m.}\\


Jdou~zástupy~věrných~s~jásotem~a~chválou,\\
my~též~do~Betléma~pospíchejme.\\
Vítejme~Pána,~Krále~andělského,\\
Ježíši~zrozenému,~Ježíši~zrozenému,\\
Ježíši~zrozenému~zpívejme.\\


Nun~freut~euch,~ihr~Christen,~singet~Jubellieder\\
und~kommet,~o~kommet~nach~Bethlehem.\\
Christus,~der~Heiland,~stieg~zu~uns~hernieder.\\
Kommt,~lasset~uns~anbeten;~Kommt,~lasset~uns~anbeten;\\
Kommt,~lasset~uns~anbeten~den~König,~den~Herrn.\\


O~come,~all~ye~faithful,~joyful~and~triumphant,\\
O~come~ye,~O~come~ye,~to~Bethlehem.\\
Come~and~behold~Him,~born~the~King~of~angels;\\
O~come,~let~us~adore~Him,~O~come,~let~us~adore~Him,\\
O~come,~let~us~adore~Him,~Christ~the~Lord.\\

\addcontentsline{toc}{section}{Ej padá padá rosenka}
\section*{Ej padá padá rosenka}
\index{Ej padá padá rosenka}\typeout{Ej padá padá rosenka}\index{Blue Effect!Ej padá padá rosenka}\textit{Blue Effect}\\


\gtxchord{Dmi}{Ej~padá,~~}\gtxchord{F}{pa}\gtxchord{C}{dá~~}\gtxchord{B}{ro}\gtxchord{Ami}{sen-}\gtxchord{Dmi}{ka}\\
\gtxchord{Dmi}{Spaly~by~~}\gtxchord{F}{mo}\gtxchord{C/E}{je~~~}\gtxchord{B/D}{~~o-}\gtxchord{Ami}{čen-}\gtxchord{Dmi}{ka}\\
\gtxchord{}{/:~}\gtxchord{Fmi}{Spaly~by~~}\gtxchord{Gmi}{moje,~~}\gtxchord{Ami}{spaly~by~~}\gtxchord{Dmi}{aj~~tv}\gtxchord{Ami}{oje}\\
\gtxchord{Dmi}{Spaly~by,~}\gtxchord{F}{duša}\gtxchord{C}{~~má,~}\gtxchord{B}{o-}\gtxchord{Ami}{bo--}\gtxchord{Dmi}{je~:/}\\


Ej~padá,~padá~listopad\\
Pozdravuj~milů~nastokrát\\
\gtxchord{}{/:~Pozdravuj~milů,~holuběnku~sivů}\\
\gtxchord{}{Že~sa~už~nevrátím~nikdy~viac~:/}\\


\textit{Solo}\\


%
%----- New Song -----
\newpage\addcontentsline{toc}{section}{Angel}
\section*{Angel}
\index{Angel}\typeout{Angel}\index{Jimi Hendrix!Angel}\textit{Jimi Hendrix}\\

\textit{intro:}\\

\gtxchord{F$\sharp$9~|~E6/9sus4~|~F$\sharp$9~B9~|~E6/9~|~E6/9}{}\\
\textit{verse:}\\

\gtxchord{F$\sharp$}{Angel~}\gtxchord{C$\sharp$}{came~down~from~}\gtxchord{G$\sharp$m}{heaven~yesterday}\\
\gtxchord{B}{Stayed~with~me~just~long~enough~to~}\gtxchord{F$\sharp$}{rescue~me}\gtxchord{E}{....}\\
\gtxchord{F$\sharp$}{And~she~}\gtxchord{C$\sharp$}{told~me~a~}\gtxchord{G$\sharp$m}{story~yesterday}\\
\gtxchord{B}{A$\flat$out~the~sweet~love~between~the~moon}\\
\hspace*\fill and~the~\gtxchord{F$\sharp$}{deep~blue~}\gtxchord{E}{sea}\\
\gtxchord{D}{Then~she~spread~her~wings~high~}\gtxchord{F$\sharp$}{over~me....she~said}\\
\gtxchord{}{She's~}\gtxchord{G$\sharp$m}{gonna~}\gtxchord{A$\sharp$m}{come~back~to}\gtxchord{B}{morrow}\\
\gtxchord{B}{And~I~said....}\\
\textit{chorus:}\\
\gtxchord{E}{Fly~on~my~sweet~}\gtxchord{F$\sharp$m}{angel.........}\\
\gtxchord{C}{Fly~on~}\gtxchord{A}{through~the~}\gtxchord{D}{sky..}\gtxchord{D$\sharp$}{.......}\\
\gtxchord{E}{Fly~on~my~sweet~}\gtxchord{F$\sharp$m}{angel..........}\\
\gtxchord{C}{Tomorrow~}\gtxchord{A}{I'm~gonna~}\gtxchord{D}{be~}\gtxchord{D$\sharp$}{by~your~}\gtxchord{E}{side}\gtxchord{C}{}\gtxchord{A}{}\gtxchord{D}{}\gtxchord{D$\sharp$}{}\\

Sure~enough~this~woman~came~home~to~me\\
Silver~wings~silhouetted~against~a~child's~sunrise\\
And~my~Angel~she~said~unto~me\\
Today~is~the~day~for~you~to~rise.\\
Take~my~hand~you're~gonna~be~my~man,~you're~gonna~rise\\
Then~she~took~me~high~over~yonder\\
And~I~said..\\

\textit{chorus}
\addcontentsline{toc}{section}{Jahody mražený}
\section*{Jahody mražený}
\index{Jahody mražený}\typeout{Jahody mražený}\index{Jiří Schellinger!Jahody mražený}\textit{Jiří Schellinger}\\

\gtxchord{A}{Poslala~mě~}\gtxchord{D}{moje~dívka~}\gtxchord{A}{pro~jahody~červený,}\\
\gtxchord{G}{bez~nich~se~}\gtxchord{E}{prý~}\gtxchord{A}{nemám~vra}\gtxchord{E}{cet,~}\gtxchord{A}{tak~tu~stojím~ztrápený.}\\
\gtxchord{}{Když~se~dívám~}\gtxchord{D}{co~je~sně}\gtxchord{A}{hu,~fouká~vítr,~pálí~mráz,}\\
\gtxchord{G}{možná~že~}\gtxchord{E}{si~ho}\gtxchord{A}{lka~myslí,~}\gtxchord{E}{že~se~mi~tak~zbaví~snáz.}\\
\gtxchord{}{/:~}\gtxchord{G}{Zapomněla~}\gtxchord{A}{váže}\gtxchord{D}{ní,~na~j}\gtxchord{A}{ahody~mraže}\gtxchord{E4}{ný,}\\
\gtxchord{G}{na~jahody~}\gtxchord{A}{mraže}\gtxchord{D}{ný,~}\gtxchord{A}{v~igelitu~bale}\gtxchord{E4}{ný.~:/}\\

Pohádku~to~připomíná~o~dvanácti~měsíčkách\\
nechtěla~mi~říci~sbohem,~teď~bych~chtěla~abych~plách.\\
Mohl~bych~se~klidně~vrátit,~vím~však~že~mě~nečeká,\\
měla~mi~to~říci~sbohem,~že~jiného~ráda~má.

%
%----- New Song -----


\addcontentsline{toc}{section}{Because the Night}
\section*{Because the Night}
\index{Because the Night}\index{Bruce Springsteen and Patti Smith!Because the Night}
\textit{Bruce Springsteen and Patti Smith}\\

\gtxchord{Bm}{}\gtxchord{G}{}\gtxchord{A}{}\gtxchord{Bm}{}\gtxchord{G}{}\gtxchord{A}{}\gtxchord{Bm}{}\\

\textit{Verse:}\\

\gtxchord{Bm}{Take~me~}\gtxchord{G}{now,~baby,~}\gtxchord{A}{here~as~I~}\gtxchord{Bm}{am.}\\
\gtxchord{}{Pull~me~}\gtxchord{G}{close~try~and~}\gtxchord{A}{under}\gtxchord{Bm}{stand.}\\
\gtxchord{}{Desire~is~}\gtxchord{G}{hunger,~is~the~}\gtxchord{A}{fire~I~}\gtxchord{Bm}{breathe.}\\
\gtxchord{}{Love~is~a~}\gtxchord{G}{banquet~on~}\gtxchord{A}{which~we~}\gtxchord{Bm}{feed.}\\
\gtxchord{B$\flat$}{Come~on~n}\gtxchord{G}{ow,~try~and~}\gtxchord{D}{under}\gtxchord{A}{stand}\\
\gtxchord{}{the~}\gtxchord{Bm}{way~I~}\gtxchord{G}{feel~when~I'm~}\gtxchord{D}{in~your~}\gtxchord{A}{hand.}\\
\gtxchord{B$\flat$}{Take~my~h}\gtxchord{G}{and;~come~}\gtxchord{D}{under~}\gtxchord{A}{cover.}\\
\gtxchord{}{They~}\gtxchord{C}{can't~hurt~you~now,~}\gtxchord{Bm}{can't~hurt~you~now,~}\\
\hspace*\fill \gtxchord{F$\sharp$}{can't~hurt~you~now.}\\

\textit{Chorus:}\\

\gtxchord{Bm}{Because~the~}\gtxchord{G}{night~be}\gtxchord{D}{longs~to~}\gtxchord{A}{lovers.}\\
\gtxchord{Bm}{Because~the~}\gtxchord{G}{night~be}\gtxchord{A}{longs~to~}\gtxchord{Bm}{lust.}\\
\gtxchord{Bm}{Because~the~}\gtxchord{G}{night~be}\gtxchord{D}{longs~to~}\gtxchord{A}{lovers.}\\
\gtxchord{Bm}{Because~the~}\gtxchord{G}{night~be}\gtxchord{A}{longs~to~}\gtxchord{Bm}{us.}\\

\textit{Verse:}\\

Have~I~doubt~when~I'm~alone?\\
Love~is~a~ring~of~the~telephone.\\
Love~is~an~angel~disguised~as~lust,\\
here~in~our~bed~until~the~morning~comes.\\
Come~on~now,~try~and~understand\\
the~way~I~feel~under~your~command.\\
Take~my~hand~as~the~sun~descends.\\
They~can't~touch~you~now,~can't~touch~you~now,\\
\hspace*\fill can't~touch~you~now.\\


\textit{Repeat chorus}\\


\textit{Ending:}\\

\gtxchord{}{In~}\gtxchord{D}{love~we~}\gtxchord{A}{fell;~with~}\gtxchord{D}{doubt~the~}\gtxchord{A}{viscious~circle~}\\
\hspace*\fill\gtxchord{Bm}{turns~and~}\gtxchord{A}{burns.}\\
\gtxchord{}{With}\gtxchord{D}{out~you,~}\gtxchord{A}{oh~I~cannot~}\gtxchord{Bm}{live,}\\
\hspace*\fill for\gtxchord{A}{give~the~}\gtxchord{D}{yearning,~}\gtxchord{A}{burning}\\
\gtxchord{}{I~be}\gtxchord{G}{lieve~it's~}\gtxchord{D}{time,~too~}\gtxchord{G}{real~to~}\gtxchord{G}{feel,}\\
\gtxchord{}{so~}\gtxchord{Bm}{touch~me~}\gtxchord{G}{now,~}\gtxchord{D}{touch~me~}\gtxchord{Bm}{now,~}\gtxchord{G}{touch~me~---~}\gtxchord{F$\sharp$}{now.}\\

\textit{Repeat chorus and fade.}


%
%----- New Song -----
\newpage\addcontentsline{toc}{section}{Come Together}
\section*{Come Together}
\index{Come Together}\typeout{Come Together}\index{The Beatles!Come Together}\textit{The Beatles}\\


\gtxchord{Dm}{Here~come~old~flat~top,~He~come~grooving~up~slowly,}\\
\gtxchord{Dm}{He~got~Joo~Joo~eyeball,~He~one~holy~roller~}\\
\gtxchord{}{H}\gtxchord{A7}{e~got~~Hair~down~to~his~knee;~~}\\
\gtxchord{G7}{Got~to~be~a~joker,~he~just~do~what~he~please.~}\\


\gtxchord{Dm}{He~wear~no~shoe~shine,~he~got~toe~jam~football}\\
\gtxchord{Dm}{He~got~monkey~finger,~he~shoot~co-ca~cola}\\
\gtxchord{}{He~say,~}\gtxchord{A7}{"I~know~you,~you~know~me."~~}\\
\gtxchord{G7}{One~thing~I~can~tell~you~is~you~got~to~be~free}\\
\gtxchord{}{Come~}\gtxchord{Bm}{Together,~Right~}\gtxchord{G}{now,~o}\gtxchord{A}{ver~me}\\


He~bag~production,~He~got~wal-rus~gumboot\\
He~got~O-no~sideboard,~He~one~spinal~cracker\\
He~got~feet~down~below~his~knee\\
Hold~you~in~his~armchair,~you~can~feel~his~disease~\\
Come~together,~right~now,~~over~me\\


He~roller~coaster,~he~got~early~warning\\
He~got~muddy~water,~He~one~Mo-jo~filter\\
He~say,~"~One~and~one~and~one~is~three."\\
Got~to~be~good~looking~'cause~he~so~hard~to~see~\\
Come~together,~Right~now,~over~me\\

\addcontentsline{toc}{section}{Dětské šaty}
\section*{Dětské šaty}
\index{Dětské šaty}\typeout{Dětské šaty}\index{Petr Kalandra!Dětské šaty}\textit{Petr Kalandra}\\


\gtxchord{G}{}\gtxchord{C}{}\gtxchord{D}{}\gtxchord{G}{}\gtxchord{Emi}{}\gtxchord{C}{}\gtxchord{D}{}\gtxchord{G}{}\\


\gtxchord{Emi}{Setři~si~}\gtxchord{C}{tvář~}\gtxchord{D}{a~slzí~}\gtxchord{G}{pár}\\
\gtxchord{Emi}{a~řekni~}\gtxchord{C}{co~ti~na~tom~}\gtxchord{D}{zále}\gtxchord{G}{ží}\\
\gtxchord{Emi}{dnes~přišla~}\gtxchord{C}{chvíle~a~}\gtxchord{D}{mě~se~zdá}\gtxchord{G}{,}\\
\gtxchord{Emi}{že~dětské~šaty~jsou~ti~}\gtxchord{G}{přítěží}\\
\gtxchord{C}{čas~je~odnáší}\gtxchord{G}{}\\


\gtxchord{G}{}\gtxchord{C}{}\gtxchord{D}{}\gtxchord{G}{}\gtxchord{Emi}{}\gtxchord{C}{}\gtxchord{D}{}\gtxchord{G}{}\\


Šli~jsme~loukou,~šli~jsme~strání\\
a~dětství~odletělo~bůhví~kam\\
má~pestrost~křídel~a~dívčích~přání\\
a~nebo~jako~kytka~uvadá\\
v~nočních~zahradách\\
a~nebo~jako~kytka~uvadá\\
v~nočních~zahradách\\

~\\

\gtxchord{Emi}{Dětství~odletělo~}\gtxchord{D}{bůhví~}\gtxchord{Emi}{kam}\\
\gtxchord{Emi}{zpátky~nevrátí~se,~}\gtxchord{D}{já~ho~}\gtxchord{Emi}{znám}\\

Dětství~odletělo~bůhví~kam\\
zpátky~nevrátí~se,~já~ho~znám\\


\gtxchord{C}{nevěř~pohádkám}\gtxchord{G}{}


%
%----- New Song -----
\addcontentsline{toc}{section}{Cukrářskej učeň}
\section*{Cukrářskej učeň}
\index{Cukrářskej učeň}\typeout{Cukrářskej učeň}\index{BSP!Cukrářskej učeň}\textit{BSP}\\


\textit{1.}\\

\gtxchord{Am}{Láska~je~~}\gtxchord{C}{solí~~}\gtxchord{G}{já~se~plavím~v~mořích~~}\gtxchord{Dsus2}{rád}\\
\gtxchord{Am}{v~trámoví~~}\gtxchord{C}{bolí~~}\gtxchord{G}{hoří~slanej~~}\gtxchord{D}{prach}\\
\gtxchord{Am}{Láska~je~~}\gtxchord{C}{solí~}\gtxchord{G}{se~solnou~tyčí~slepec~~}\gtxchord{Dsus2}{plách}\\
\gtxchord{C}{pod~víčky~škrábe~~}\gtxchord{D}{šelma~vrah}\\


\textit{2.}\\

Láska~je~solí~dolům~solnejm~hrozí~krach\\
cukrářskej~učeň~s~jizvou~v~srdci~k~jiný~plách\\
Láska~se~hojí~v~kleče,~mečem~v~palbě~pravd\\
dej~mi~přízeň~zažeň~chlad\\


\textit{R:}\\

\gtxchord{G}{Hledám~lásku~a~~}\gtxchord{D}{klid~~~}\gtxchord{Am}{v~úpatí~tvejch~~}\gtxchord{C}{pyramid}\\
\gtxchord{G}{dej~mi~lásku~a~}\gtxchord{D}{stín~upro}\gtxchord{Am}{střed~tvejch~}\gtxchord{C}{džín}\\
\gtxchord{G}{Údolí~zválený~}\gtxchord{D}{uprostřed~}\gtxchord{Am}{tvejch~dlouhejch~}\gtxchord{C}{stínů}\\
\gtxchord{}{údolí~zválený~}\gtxchord{Am}{tvejch~džín~~}\gtxchord{Em}{(tvejch~džín)}\\


\textit{3. = 1.}\\

\textit{R:}\\
Až~k~vám~ty~zprávy~o~nás~dojdou\\
ty~zprávy~z~dálnejch~moří~až~k~vám~dojdou\\
Až~k~vám~ty~zprávy~v~láhvích~dojdou\\
ty~zprávy~z~dálnejch~moří~až~k~vám~dojdou\\
Až~k~vám~ty~zprávy~v~láhvích~dojdou\\
že~sůl~se~lásce~dvoří~šelmám~v~klecích~přej~\\
svobodu~go~go\\
Až~k~vám~ty~zprávy~o~nás~dojdou\\
ty~vůně~dálnejch~moří~kolem~projdou~jdou~jdou~...\\


\textit{solo}\\


\textit{R:}\\
Hledám~lásku~a~klid~v~úpatí~tvejch~pyramid\\
dej~mi~lásku~a~stín~uprostřed~tvejch~jeans\\
Hledám~lásku~a~klid~máš~to~co~chci~mít\\
v~tobě~lásko~můj~stín~chci~skrýt\\




%
%----- New Song -----
\newpage\addcontentsline{toc}{section}{Danny Boy}
\section*{Danny Boy}
\index{Danny Boy}\typeout{Danny Boy}

\gtxchord{}{Oh~Danny~boy,~the~}\gtxchord{C}{pipes,~the~pipes~are~}\gtxchord{F}{calling~}\\
\gtxchord{}{From~glen~to~glen,~and~}\gtxchord{C}{down~the~mountain~}\gtxchord{G}{side~}\\
\gtxchord{}{The~summer's~}\gtxchord{C}{gone,~and~all~the~roses~}\gtxchord{F}{falling~}\\
\gtxchord{}{'Tis~you~must~go,~'tis~you~must~}\gtxchord{C}{go~and~}\gtxchord{G}{I~must~}\gtxchord{C}{bide~}\\


\gtxchord{}{But~come}\gtxchord{C}{~ye~back~when~}\gtxchord{F}{summer's~in~the~}\gtxchord{C}{meadow~}\\
\gtxchord{}{Or~when~the~}\gtxchord{Am}{valley's~hushed~and~}\gtxchord{F}{white~with~}\gtxchord{G}{snow~}\\
\gtxchord{}{'Tis~I'll~be~}\gtxchord{C}{there~in~}\gtxchord{F}{sunshine~or~in~}\gtxchord{C}{shadow}\gtxchord{Am}{~}\\
\gtxchord{}{Oh~Danny~boy,~oh~Danny~}\gtxchord{C}{boy,~I~}\gtxchord{G}{love~you~}\gtxchord{C}{so~}\\


But~if~you~come,~and~all~the~flowers~are~dying~\\
If~I~am~dead,~as~dead~I~may~well~be~\\
You'll~come~and~find~the~place~where~I~am~lying~\\
And~kneel~and~say~an~"Ave"~there~for~me~\\


And~I~shall~hear,~tho'~soft~you~tread~above~me~\\
And~all~my~grave~shall~warm~and~sweeter~be~\\
If~you~will~bend~and~tell~me~that~you~love~me~\\
Then~I~will~sleep~in~peace~until~you~come~to~me\\






%
%----- New Song -----


%
%----- New Song -----
\addcontentsline{toc}{section}{?Dónde están los ladrones?}
\section*{?Dónde están los ladrones?}
\index{Donde estan los ladrones@?Dónde están los ladrones?}\typeout{?Dónde están los ladrones?}\index{Shakira!?Dónde están los ladrones?}\textit{Shakira}\\

\gtxchord{}{Los~han~visto}\gtxchord{A}{~por~ahí}\\
\gtxchord{}{Los~han~visto}\gtxchord{Bm}{~en~los~tejados}\\
\gtxchord{}{Dando~vueltas~en~Pa}\gtxchord{D}{rís}\\
\gtxchord{}{Condenando~en~los~juz}\gtxchord{E}{gados}\\

\gtxchord{}{Con~la~nariz~empo}\gtxchord{A}{lvada}\\
\gtxchord{}{De~corbat}\gtxchord{Bm}{a~o~de~blue~jeans}\\
\gtxchord{}{Los~han~visto~en}\gtxchord{D}{~las~portadas~todas}\\
\gtxchord{}{Sin~más~nada~que~de}\gtxchord{E}{cir}\\

\textit{Chorus:}\\
\gtxchord{}{Dónde~están~los~la}\gtxchord{Fm}{dro}\gtxchord{G$\sharp$}{nes}\gtxchord{A*}{}\\
\gtxchord{}{Dónde~está~el~ase}\gtxchord{Fm}{sin}\gtxchord{G$\sharp$}{o}\gtxchord{A*}{}\\
\gtxchord{}{Quizá~allá~revolcá}\gtxchord{Bm}{ndo}\gtxchord{C$\sharp$}{se~}\gtxchord{D*}{~~en~el~patio~del~vecino}\\
\gtxchord{}{Y~qué~pasa~si~son~}\gtxchord{Fm}{ell}\gtxchord{G$\sharp$}{os}\gtxchord{A*}{}\\
\gtxchord{}{Y~qué~pasa~si~soy~}\gtxchord{Fm}{yo}\gtxchord{G$\sharp$}{}\gtxchord{A*}{}\\
\gtxchord{}{El~que~toca~esta~}\gtxchord{Bm}{gui}\gtxchord{C$\sharp$}{tarr}\gtxchord{D*}{a}\\
\gtxchord{}{O~la~que~canta~e}\gtxchord{E}{sta~canción}\\
\gtxchord{}{La~que~canta~e}\gtxchord{D}{sta~}\gtxchord{C$\sharp$}{canci}\gtxchord{Bm}{ón}\gtxchord{D}{}\gtxchord{C$\sharp$}{}\gtxchord{Bm}{}\\

Los~han~visto~de~rodillas\\
Sentados~o~de~cuclillas\\
Parados~dando~lecciones\\
En~todas~las~posiciones\\

Predicando~en~las~iglesias\\
Hasta~ofreciendo~conciertos\\
Los~han~visto~en~los~cocteles~todos\\
Repartiendo~ministerios\\

\textit{Chorus}
%
%----- New Song -----



%
%----- New Song -----
\addcontentsline{toc}{section}{Follow Me up to Carlow}
\section*{Follow Me up to Carlow}
\index{Follow Me up to Carlow}\typeout{Follow Me up to Carlow}

\gtxchord{Em}{Lift~Mac~Cahir~Og~your~face,}\\
\hspace*\fill ~brooding~o'er~the~\gtxchord{D}{old~disgrace~}\\
\gtxchord{}{That~}\gtxchord{Em}{black~Fitzwilliam~stormed~your~place}\\
\hspace*\fill and~drove~you~\gtxchord{D}{to~the~}\gtxchord{Em}{Fern.}\\
\gtxchord{Em}{Gray~said~victory~was~sure,~soon~the~firebrand~}\gtxchord{D}{he'd~secure}\\
\gtxchord{}{Un}\gtxchord{Em}{til~he~met~at~Glenmalure,~Fiach~Mac~}\gtxchord{D}{Hugh~O'}\gtxchord{Em}{Byrne}\\


\textit{Chorus:}\\

\gtxchord{Bm}{Curse~and~swear,~Lord~Kildare,~}\\
\gtxchord{D}{Fiach~will~do~what~Feach~will~dare}\\
\gtxchord{Bm}{Now~Fitzwilliam~have~a~care,~}\\
\gtxchord{D}{fallen~is~your~}\gtxchord{Em}{star~low}\\
\gtxchord{Bm}{Up~with~halbert,~out~with~sword,~}\\
\gtxchord{D}{on~we~go~for~by~the~Lord}\\
\gtxchord{Bm}{Fiach~Mac~Hugh~has~given~his~word:~}\\
\gtxchord{D}{Follow~me~up~to~}\gtxchord{Em}{Carlow~}\\


See~the~swords~of~Glen~Imayle\\
\hspace*\fill flashing~o'er~the~English~Pale\\
See~all~the~children~of~the~Gael,\\
\hspace*\fill beneath~O'Byrne's~banners\\
Rooster~of~the~fighting~stock,\\
\hspace*\fill would~you~let~an~English~cock\\
Crow~out~upon~an~Irish~rock,\\
\hspace*\fill fly~up~and~teach~him~manners\\

\textit{Chorus:}\\


From~Tassagart~to~Clonmore~flows~a~stream~of~Saxon~Gore\\
Great~is~Rory~Og~O'More~at~sending~loons~to~Hades.\\
White~is~sick~and~Lane~is~fled,~now~for~black~Fitzwilliams~head\\
We'll~send~it~over,~dripping~red,~to~Liza~and~her~ladies\\

\textit{Chorus:}\\


%
%----- New Song -----
%
%----- New Song -----
\newpage\addcontentsline{toc}{section}{Gyongháju Lány}
\section*{Gyongháju Lány}
\index{Gyongháju Lány}\typeout{Gyongháju Lány}\index{Omega!Gyongháju Lány}\textit{Omega}\\


\textit{4x:}\\\hspace*{5mm}\gtxchord{Fm~Eb~Bbm~Fm}{}\\
\textit{2x:}\\\hspace*{5mm}\gtxchord{G$\sharp$~Eb~Bbm~Fm}{}\\

\textit{Verse:}\\

\gtxchord{Fm}{Egyszer~a~n}\gtxchord{E$\flat$}{ap~}\gtxchord{B$\flat$m}{Úgy~elfára}\gtxchord{Fm}{dt,}\\
\gtxchord{Fm}{Elaludt~mé}\gtxchord{E$\flat$}{ly,~}\gtxchord{B$\flat$m}{Zöld~tó~öl}\gtxchord{Fm}{én,~}\\
Az~embereknek~Fájt~a~sötét,~\\
O~megsajnált,~Eljött~közénk~\\

\textit{Chorus:}\\

\gtxchord{}{Igen,~}\gtxchord{G$\sharp$}{jött~egy~gyöngyhajú~}\gtxchord{E$\flat$}{lány,}\\
\gtxchord{B$\flat$m}{Álmodtam,~vagy~igaz~}\gtxchord{Fm}{talán,}\\
\gtxchord{G$\sharp$}{Így~lett~a~föld,~az~}\gtxchord{E$\flat$}{ég~}\\
\gtxchord{B$\flat$m}{Zöld~meg~kék,~mint~}\gtxchord{Fm}{rég.}\\


\section*{Dívka s perlami ve vlasech}
\index{Dívka s perlami ve vlasech}\typeout{Dívka s perlami ve vlasech}\index{Aleš Brichta!Dívka s perlami ve vlasech}
\textit{Aleš Brichta}\\

\textit{1. }\\
Zas~mě~tu~máš,~nějak~se~mračíš,\\
vybledlej~smích~už~ve~dveřích,\\
s~čelenkou~z~perel~svatozář~ztrácíš,\\
kolik~se~platí~za~vláčnej~hřích.\\

\textit{R:}\\
No~tak,~lásko,~co~chceš~mi~říct,\\
máš~už~perly,~možná~i~víc,\\
lásko,~na~co~se~ptáš, svíčku~zhasínáš.\\

Nemám,~lásko,~co~bych~ti~dal, \\
chtělas~všechno, nebyl~jsem~král,\\
lásko,~na~co~se~ptáš, \\
perly~ve~vlasech~máš.\\

\textit{2. }\\
Tvý~horký~rty,~víc~radši~ne,\\
nejsou~už~mý,~nejsi~má~Cher,\\
něco~snad~chápu,~to~ne,~to~ne,\\
bolí~to,~hořím,~jak~černej~tér.\\

No~tak,~lásko,~kdo~mi~tě~vzal,\\
komus~dala~tělo~i~duši,\\
lásko,~na~co~je~pláč,\\
když~to~skončit~má.\\

Vždyť~už,~lásko,~svý~perly~máš,\\
tak~proč~padaj,~měněj~se~v~slzy,\\
lásko,~na~co~je~pláč,\\
perly~ve~vlasech~máš.\\

No~tak,~lásko,~co~chceš~mi~říct,~...\\

\textit{3. }\\
Chtěla~jsi~víc~pro~svoje~touhy,\\
já,~chudej~princ,~mám,~jen~co~mám,\\
co~vlastně~zbývá,~jen~slzy~pouhý\\
ze~svatebních~zvonů,~z~nebeskejch~bran.\\

No~tak,~lásko,~kdo~mi~tě~vzal,~...\\

No~tak,~lásko,~co~chceš~mi~říct,~...\\

\addcontentsline{toc}{section}{René, já a Rudolf}
\section*{René, já a Rudolf}
\index{René, já a Rudolf}\typeout{René, já a Rudolf}\index{Jiří Schellinger!René, já a Rudolf}\textit{Jiří Schellinger}\\


\gtxchord{G}{Nedělní~odpoledne~}\gtxchord{Am}{stane~se~}\gtxchord{C}{pro~mnohé~chvílí~}\gtxchord{G}{volna,}\\
\gtxchord{G}{někdo~si~běhá~jen~tak~}\gtxchord{Am}{po~lese,~}\gtxchord{C}{jiný~zas~chodí~}\gtxchord{G}{zvolna.}\\
\gtxchord{G7}{My~však~neznáme~rozkoš~}\gtxchord{C}{oddychu~}\gtxchord{Cm7}{a~sportujeme~v~}\gtxchord{G}{houfu,}\\
\gtxchord{G}{nikde~nejmenší~známky~}\gtxchord{Am}{po~břichu,~}\gtxchord{C}{my~propadli~jsme~}\gtxchord{G}{golfu.}\\


\gtxchord{G}{René,~já~a~Rudolf~chodíváme~na~golf,}\\
\gtxchord{Am}{René,~já~a~Rudolf~}\gtxchord{D7}{chodíváme~na~golf,}\\
\gtxchord{G}{René,~já~a~Rudolf~chodíváme~na~golf,}\\
\gtxchord{Am}{René,~já~a~Rudolf~}\gtxchord{D7}{chodíváme~na~golf.}\\


Nedělní~odpoledne~stane~se~pro~mnohé~chvílí~nudy,\\
někdo~to~pomyšlení~nesnese~a~tak~jde~válet~sudy.\\
Věřte,~že~nás~už~vůbec~nevábí~ve~tvářích~dívek~důlky,\\
můžou~mít~vlasy~jako~hedvábí~nám~stačí~řádné~hůlky.\\


René,~já~a~Rudolf,~chodíváme~na~golf,\\
René,~já~a~Rudolf,~chodíváme~na~golf,\\
René,~já~a~Rudolf,~chodíváme~na~golf,\\
René,~já~a~Rudolf,~chodíváme~na~golf.\\


\newpage\addcontentsline{toc}{section}{Griechischer Wein}
\section*{Griechischer Wein}
\index{Griechischer Wein}\typeout{Griechischer Wein}\index{Udo Jürgens!Griechischer Wein}\textit{Udo Jürgens}\\

\textit{1.}\\

\gtxchord{}{Es~war~schon~}\gtxchord{Cm}{dunkel,}
\\~als~ich~durch~die~Vorstadtstraßen~\gtxchord{G$\sharp$}{heim}\gtxchord{A$\sharp$}{wärts~}\gtxchord{D$\sharp$}{ging.~}\\
\gtxchord{}{Da~war~ein~Wirtshaus,}\\
~aus~dem~das~Licht~noch~auf~den~\gtxchord{Fm}{Gehsteig~}\gtxchord{A$\sharp$}{schien.}\\
\gtxchord{}{Ich~hatte~}\gtxchord{Cm}{Zeit~und~mir~war~}\gtxchord{G7}{kalt,~drum~trat~ich~}\gtxchord{Cm}{ein.~}\\
\gtxchord{}{Da~saßen~Männer~mit~braunen~Augen}\\
und~mit s\gtxchord{G$\sharp$}{chwarz}\gtxchord{A$\sharp$}{em~H}\gtxchord{D$\sharp$}{aar~},\\
\gtxchord{}{und~aus~der~Jukebox}\\
~erklang~Musik~die~fremd~und \gtxchord{Fm}{südlich~}\gtxchord{A$\sharp$}{war.~}\\
\gtxchord{}{Als~man~mich~}\gtxchord{Cm}{sah,~stand~einer~}\gtxchord{G7}{auf~und~lud~mich~}\gtxchord{Cm}{ein.~}\\


\textit{R:}\\

\gtxchord{G$\sharp$}{Griechischer~Wein~ist~so~wie~das~Blut~der~Erde,~}\\
\gtxchord{D$\sharp$}{komm~schenk~dir~ein,~}\gtxchord{}{und~wenn~ich~dann~traurig~werde~}\\
\gtxchord{A$\sharp$7}{liegt~es~daran,~}\gtxchord{}{dass~ich~immer~träume~von~}\gtxchord{D$\sharp$}{daheim,}\\
~du~musst~ver\gtxchord{D$\sharp$7}{zeihn.~}\\
\gtxchord{G$\sharp$}{Griechischer~Wein~und~die~altvertrauten~Lieder,}\\
~sc\gtxchord{D$\sharp$}{henk~noch~mal~ein,~}\gtxchord{}{denn~ich~fühl~die~Sehnsucht~wieder,~}\\
\gtxchord{A$\sharp$7}{in~dieser~Stadt~}\gtxchord{}{werd~ich~immer~nur~ein~Fremder~}\gtxchord{Cm}{sein,~}\\
\gtxchord{G7}{---~und~al}\gtxchord{Cm}{lein.~}\\

\textit{2.}\\
Und~dann~erzählten\\
sie~mir~von~grünen~Hügeln, Meer~und~Wind,~\\
von~alten~Häusern\\
und~jungen~Frauen,~die~alleine~sind~\\
und~von~dem~Kind,~das~seinen~Vater~noch~nie~sah.~\\
Sie~sagten~sich\\
immer~wieder~irgendwann~geht~es~zurück,~\\
und~das~Ersparte\\
genügt~zu~Hause~für~ein~kleines~Glück,~\\
und~bald~denkt~keiner~mehr~daran,~wie~es~hier~war.~\\

\textit{R:}



%
%----- New Song -----
\newpage\addcontentsline{toc}{section}{Hallelujah}
\section*{Hallelujah}
\index{Hallelujah}\typeout{Hallelujah}\index{Leonard Cohen!Hallelujah}\textit{Leonard Cohen}\\


\gtxchord{C}{}\gtxchord{Am}{}\gtxchord{C}{}\gtxchord{Am}{}\\


\gtxchord{}{Now~I've~}\gtxchord{C}{heard~there~was~a~}\gtxchord{Am}{secret~chord~}\\
\gtxchord{}{That~}\gtxchord{C}{David~played,~and~it~}\gtxchord{Am}{pleased~the~Lord~}\\
\gtxchord{}{But~}\gtxchord{F}{you~don't~really~}\gtxchord{G}{care~for~music,~do~}\gtxchord{C}{you?~}\gtxchord{F}{}\gtxchord{G}{}\\
\gtxchord{C}{It~goes~like~this~}\\
\gtxchord{}{The~}\gtxchord{F}{fourth,~the~}\gtxchord{G}{fifth~}\\
\gtxchord{}{The~}\gtxchord{Am}{minor~fall,~the~}\gtxchord{G}{major~lift~}\\
\gtxchord{}{The~}\gtxchord{E7}{baffled~king~composing~Halle}\gtxchord{Am}{lujah~}\\
\gtxchord{F}{Hallelujah~}\gtxchord{Am}{Hallelujah~}\\
\gtxchord{F}{Hallelujah~}\gtxchord{Am}{Halle}\gtxchord{G}{lu-}\gtxchord{C}{jah~}\\


Your~faith~was~strong~but~you~needed~proof~\\
You~saw~her~bathing~on~the~roof~\\
Her~beauty~and~the~moonlight~overthrew~her~\\
She~tied~you~\\
To~a~kitchen~chair~\\
She~broke~your~throne,~and~she~cut~your~hair~\\
And~from~your~lips~she~drew~the~Hallelujah~\\


Hallelujah,~Hallelujah~\\
Hallelujah,~Hallelujah~\\


You~say~I~took~the~name~in~vain~\\
I~don't~even~know~the~name~\\
But~if~I~did,~well~really,~what's~it~to~you?~\\
There's~a~blaze~of~light~\\
In~every~word~\\
It~doesn't~matter~which~you~heard~\\
The~holy~or~the~broken~Hallelujah~\\


Hallelujah,~Hallelujah~\\
Hallelujah,~Hallelujah~\\


I~did~my~best,~it~wasn't~much~\\
I~couldn't~feel,~so~I~tried~to~touch~\\
I've~told~the~truth,~I~didn't~come~to~fool~you~\\
And~even~though~\\
It~all~went~wrong~\\
I'll~stand~before~the~Lord~of~Song~\\
With~nothing~on~my~tongue~but~Hallelujah~\\


Hallelujah,~Hallelujah~\\
Hallelujah,~Hallelujah~\\




%
%----- New Song -----
\newpage\addcontentsline{toc}{section}{Ironic}
\section*{Ironic}
\index{Ironic}\typeout{Ironic}\index{Alanis Morissette!Ironic}\textit{Alanis Morissette}\\


\gtxchord{G}{An~o}\gtxchord{C}{ld~m}\gtxchord{G}{an~turned~nine}\gtxchord{Am}{ty-eight}\\
\gtxchord{}{he~won~the~}\gtxchord{G}{lotte}\gtxchord{C}{ry~and~}\gtxchord{G}{died~the~next~d}\gtxchord{Am}{ay.}\\


It's~a~black~fly~in~your~chardonnay,\\
it's~a~death~row~pardon~two~minutes~to~late.\\
Isn't~it~ironic...~don't~you~think?\\


\textit{chorus:}\\

\gtxchord{}{It's~like~}\gtxchord{G}{rain~}\gtxchord{C}{on~your}\gtxchord{G}{~wedding~day,}\gtxchord{Am}{}\\

it's~a~free~ride~when~you've~already~paid,\\

it's~the~good~advice~that~you~just~didn't~take,\\

\gtxchord{B$\flat$}{who~would~have~th}\gtxchord{F}{ought...~it~}\gtxchord{G}{figures.}\\


Mr.~play-it-safe~was~afraid~to~fly,\\
he~packed~his~suitcase~and~kissed~his~kids~good-bye.\\
He~waited~his~whole~damn~life~just~to~take~that~flight\\
and~as~the~plane~crashed~down\\
\hspace*\fill ~he~thought~"well~isn't~this~nice...".
And~isn't~it~ironic...~don't~you~think?\\


\gtxchord{}{Well~}\gtxchord{F}{life~has~a~funny~way~of~sneaking~}\gtxchord{G}{up~on~you,}\\
\gtxchord{}{when~}\gtxchord{F}{you~think~everything~is~okay}\\
~and~\gtxchord{G}{everything's~going~right.}\\
\gtxchord{}{And~l}\gtxchord{F}{ife~has~a~funny~way~of~helping~yo}\gtxchord{G}{u~out}\\
when\gtxchord{}{you~t}\gtxchord{F}{hink~everything's~gone~wrong}\\
and~everything~blows~up~in~your~face.\\

A~traffic~jam~when~you~are~already~late,\\
a~no-smoking~sign~on~your~cigarette~break.\\
It's~like~ten~thousand~spoons~when~all~you~need~is~a~knife,\\
it's~like~meeting~the~man~of~my~dreams~then~meeting~his~beautiful~wife.\\
And~isn't~it~ironic...~don't~you~think?\\
a~little~too~ironic...~and~yeah~i~really~do~think...\\

\gtxchord{}{L}\gtxchord{C}{ife~has~a~funny~way~of~sneaking~up~on}\gtxchord{G}{~you,}\\
\gtxchord{}{l}\gtxchord{C}{ife~has~a~funny,~funny~way~~of~helpi}\gtxchord{G}{ng~you~out}\\
\gtxchord{C}{--~helping~you~out.}\\


%
%----- New Song -----



%
%----- New Song -----
\newpage\addcontentsline{toc}{section}{Jim Bridger}
\section*{Jim Bridger}
\index{Jim Bridger}\typeout{Jim Bridger}\index{Johnny Horton!Jim Bridger}\textit{Johnny Horton}\\


\textit{1.}\\

\gtxchord{Am}{Once~there~was~a~mountain~man}\\
who~couldn’t~write~his~name,\\
\gtxchord{}{yet~he~deserves~a~front~row~seat}\\
~in~\gtxchord{Dm}{history’s~hall~of~fame.}\\
\gtxchord{}{He~for}\gtxchord{Am}{got~more~about~the~Indians}\\
than~\gtxchord{Dm}{we~will~ever~know,}\\
\gtxchord{}{he~}\gtxchord{Am}{spoke~the~language~of~the~Sioux~-~-}\\
\gtxchord{}{the~}\gtxchord{E}{Blackfoot~and~the~}\gtxchord{Am}{Crow.}\\


\textit{ }\\
\gtxchord{}{Let’s~}\gtxchord{A}{drink~to~old~Jim~Bridger,~yes,~}\gtxchord{E}{lift~your~glasses~high,}\\
\gtxchord{}{as~long~as~there’s~a~USA,~don’t~}\gtxchord{E7}{let~his~memory~}\gtxchord{A}{die.}\\
\gtxchord{}{That~he~was~making~history,~never~}\gtxchord{A7}{once~occurred~to~}\gtxchord{D}{him,}\\
\gtxchord{}{but~I~}\gtxchord{E}{doubt~if~we’d~a~been~here,~if~it}\gtxchord{E7}{~weren’t~for~men~like~}\gtxchord{Am}{Jim.}\\


\textit{2. }\\
He~spoke~with~General~Custer\\
and~said,~“Listen,~Yellow~Hair,\\
the~Sioux~were~a~great~nation,\\
so~treat~them~fair~and~square.\\
Sit~in~on~their~war~council,\\
don’t~laugh~away~their~pride,\\
but~Custer~didn’t~listen,\\
at~Little~Big~Horn~Custer~died.\\


\textit{3. }\\
There’s~poems~and~there’s~legends\\
that~tell~of~Carson’s~fame,\\
yet~compared~to~Jim~Bridger,\\
Kit~was~civilized~and~tame.\\
These~words~are~straight~from~Carson’s~lips,\\
if~you~place~such~store~by~him,\\
if~there’s~a~man~who~knows~~this~gun~–\\
forsaken~land~it’s~Jim.

%
%----- New Song -----

%
%----- New Song -----
\newpage\addcontentsline{toc}{section}{Šípková Růženka}
\section*{Šípková Ruženka}
\index{Szipkova Ruzenka@Šípková Růženka}\typeout{Šípková Ruženka}\index{Jiří Schellinger!Šípková Růženka}\textit{Jiří Schellinger}\\


\textit{1.}\\
\gtxchord{}{Ještě~}\gtxchord{Gm}{spí~a~spí~a~spí~zámek~}\gtxchord{F}{šípkový}\\
\gtxchord{Gm}{žádný~princ~tam~v~lesích,~}\gtxchord{Dm}{ptáky~neloví}\\

Ještě~spí~a~spí~a~spí~dívka~zakletá\\

u~lůžka~jí~planá~růže~rozkvétá\\

\gtxchord{B}{To~se~}\gtxchord{C}{schválně~dětem~}\gtxchord{Gm}{říká}\\
\gtxchord{D$\sharp$}{aby~s~}\gtxchord{F}{důvěrou~šli~}\gtxchord{B}{spát,klidně~}\gtxchord{Dm}{spát,}\\
\gtxchord{}{že~se~}\gtxchord{Gm}{dům~probou}\gtxchord{F}{zí}\\
\gtxchord{}{a~ta~}\gtxchord{B}{kráska~proci}\gtxchord{D$\sharp$}{tá}\\
\gtxchord{}{Zatím~}\gtxchord{Cm}{spí~tam~}\gtxchord{Dm}{dál,~spí~tam~v~}\gtxchord{Gm}{růžích.}\\


\textit{2.}\\
Kdo~jí~ústa~k~ústum~dá,~kdo~ji~zachrání\\
kdo~si~dívku~pobledlou~vezme~za~paní.\\
Vyjdi~zítra~za~ní~a~nevěř~pohádkám\\
žádny~princ~už~není,~musíš~tam~jít~sám.\\


To~se~schválně~dětem~říká\\
aby~s~důvěrou~šli~spát,~klidně~spát\\
že~se~dům~probouzí~a~ta~kráska~procitá\\
Zatím~spí~tam~dál,~spí~v~růžích.\\


\gtxchord{Gm}{Musíš~přijít~}\gtxchord{F}{sám,}\\
\gtxchord{}{nesmíš~}\gtxchord{B}{věřit~pohád}\gtxchord{D$\sharp$}{kam}\\
\gtxchord{Cm}{čeká~dívka~}\gtxchord{F}{dál,~spí~tam~v~}\gtxchord{Gm}{růžích,}\\
\gtxchord{Cm}{čeká~dívka~}\gtxchord{F}{dál,~spí~tam~v~}\gtxchord{Gm}{růžích.}\\




%
%----- New Song -----
\addcontentsline{toc}{section}{Smoke on the Water}
\section*{Smoke on the Water}
\index{Smoke on the Water}\typeout{Smoke on the Water}\index{Deep Purple!Smoke on the Water}\textit{Deep Purple}\\

\textit{6x:}\\
\hspace*{5mm}\gtxchord{A~C~D~A~C~Eb~A~C~D~C~A}{}

\gtxchord{}{We~}\gtxchord{Am}{all~came~out~to~montreux}\\
\gtxchord{}{On~the~l}\gtxchord{C}{ake~gen}\gtxchord{D}{eva~s}\gtxchord{Am}{horeline}\\
\gtxchord{Am}{To~make~records~with~a~mobile}\\
\gtxchord{}{We~d}\gtxchord{C}{idn't~h}\gtxchord{D}{ave~much~}\gtxchord{Am}{time}\\
\gtxchord{Am}{Frank~zappa~and~the~mothers}\\
\gtxchord{}{Were~}\gtxchord{C}{at~the~best~pl}\gtxchord{D}{ace~a}\gtxchord{D}{round}\\
\gtxchord{Am}{But~some~stupid~with~a~flare~gun}\\
\gtxchord{C}{Burned~the~place~}\gtxchord{D}{to~the~}\gtxchord{Am}{ground}\\
\gtxchord{D}{Smoke~on~the~w}\gtxchord{F}{ater,}\gtxchord{Am}{~fire~}\gtxchord{C}{in~the~}\gtxchord{Am}{sky}\\
\gtxchord{D}{Smoke~on~the~w}\gtxchord{F}{ater...}\\


\textit{2x Riff:}\\


They~burned~down~the~gambling~house\\
It~died~with~an~awful~sound\\
Funky~claude~was~running~in~and~out\\
Pulling~kids~out~the~ground\\
When~it~all~was~over\\
We~had~to~find~another~place\\
But~swiss~time~was~running~out\\
It~seemed~that~we~would~lose~the~race\\
Smoke~on~the~water,~fire~in~the~sky\\


We~ended~up~at~the~grand~hotel\\
It~was~empty~cold~and~bare\\
But~with~the~rolling~truck~stones~thing~just~outside\\
Making~our~music~there\\
With~a~few~red~lights~and~a~few~old~beds\\
We~make~a~place~to~sweat\\
No~matter~what~we~get~out~of~this\\
I~know~we'll~never~forget\\
Smoke~on~the~water,~fire~in~the~sky\\




%
%----- New Song -----
\addcontentsline{toc}{section}{The Last Unicorn}
\section*{The Last Unicorn}
\index{The Last Unicorn}\typeout{The Last Unicorn}\index{America!The Last Unicorn}\textit{America}\\


\gtxchord{}{When~the~}\gtxchord{Am}{last~eagle~flies~over~the~}\gtxchord{F}{last~crumbling~}\gtxchord{G}{mountain}\\
\gtxchord{}{And~the~}\gtxchord{Am}{last~lion~roars~at~the~}\gtxchord{F}{last~dusty~}\gtxchord{G}{fountain}\\
\gtxchord{}{In~the~}\gtxchord{Am}{shadow~of~the~}\gtxchord{Em}{forest,~though~she~}\gtxchord{F}{may~be~old~and~}\gtxchord{C}{worn}\\
\gtxchord{}{They~will~}\gtxchord{F}{stare~un}\gtxchord{C}{believing} \gtxchord{}{at~the~}\gtxchord{F}{last~uni}\gtxchord{G}{corn~}\gtxchord{N.C.}{}\\

When~the~first~breath~of~winter\\
\hspace*\fill through~the~flowers~is~icing\\
And~you~look~to~the~north~and~a~pale~moon~is~rising\\
And~it~seems~like~all~is~dying\\
\hspace*\fill and~would~leave~the~world~to~mourn\\
In~the~distance~hear~her~laughter of~the~last~unicorn\\


\gtxchord{}{I'm~a}\gtxchord{C}{li}\gtxchord{Am}{ve--------I'm~a}\gtxchord{G}{live}\gtxchord{Am}{}\gtxchord{Em}{}\gtxchord{F}{}\gtxchord{G}{}\\


When~the~last~moon~is~cast~over~the~last~star~of~morning\\
And~~the~future~is~past\\
\hspace*\fill without~even~a~last~desperate~warning\\
Then~look~into~the~sky\\
\hspace*\fill where~through~the~clouds~a~path~is~formed\\
Look~and~see~her~how~she~sparkles It's~the~last~unicorn\\


\gtxchord{}{I'm~a}\gtxchord{C}{live-}\gtxchord{Am}{-------I'm~a}\gtxchord{G}{live}\gtxchord{C}{---}\gtxchord{Am7}{-----------I'm~}\gtxchord{G}{aliv}\gtxchord{Am}{e}\gtxchord{Em}{}\gtxchord{F}{}\gtxchord{G}{}

\gtxchord{Am}{}\gtxchord{Em}{}\gtxchord{F}{}\gtxchord{G}{}\\


%
%----- New Song -----
\newpage\addcontentsline{toc}{section}{Whiskey In The Jar}
\section*{Whiskey In The Jar}
\index{Whiskey In The Jar}\typeout{Whiskey In The Jar}



\gtxchord{Am}{}\gtxchord{G}{}\gtxchord{Em}{}\\


\textit{1. }\\
\gtxchord{}{As~I~}\gtxchord{G}{was~goin'~over,~the~Cork~and~Ke}\gtxchord{Em}{rry~mountains~}\\
\gtxchord{}{I~sa}\gtxchord{C}{w~Captain~Farrell,~and~his~money~he~was~c}\gtxchord{G}{ountin'~}\\
\gtxchord{}{I~fi}\gtxchord{G}{rst~produced~my~pistol,~and~then~produced~m}\gtxchord{Em}{y~rapier~}\\
\gtxchord{}{I~said~stan}\gtxchord{C}{d~and~deliver,~or~the~devil~he~may~ta}\gtxchord{G}{ke~ya~~}\\


\textit{R:}\\
\gtxchord{}{Musha~ring~d}\gtxchord{D}{um~a~do~dum~a~dah~}\\
\gtxchord{C}{Whack~for~my~daddy-o~}\\


Whack~for~my~daddy-o~\\
\gtxchord{}{There's~whisk}\gtxchord{G}{ey~in~the~jar-o~~}\\


\textit{2.}\\
I~took~all~of~his~money,~and~it~was~a~pretty~penny~\\
I~took~all~of~his~money,~and~I~brought~it~home~to~Molly~\\
She~swore~that~she~loved~me,~never~would~she~leave~me~\\
But~the~devil~take~that~woman,~for~you~know\\
\hspace*\fill she~tricked~me~easy~~\\

\textit{R:}\\
Musha~ring~dum~a~do~dum~a~dah~\\
Whack~for~my~daddy-o~\\
Whack~for~my~daddy-o~\\
There's~whiskey~in~the~jar-o~~\\


\textit{3.}\\
Being~drunk~and~weary,~I~went~to~Molly's~chamber~\\
Takin'~my~money~with~me,~and~I~never~knew~the~danger~\\
For~about~six~or~maybe~seven,~in~walked~Captain~Farrell~\\
I~jumped~up,~fired~off~my~pistols,\\
\hspace*\fill and~I~shot~him~with~both~barrels~~\\


\textit{R:}\\
Musha~ring~dum~a~do~dum~a~dah~\\
Whack~for~my~daddy-o~\\
Whack~for~my~daddy-o~\\
There's~whiskey~in~the~jar-o~~\\


\textit{4.}\\
Now~some~men~like~the~fishin',~and~some~men~like~the~fowlin'~\\
And~some~men~like~ta~hear,~a~cannon~ball~a~roarin'~\\
But~me~I~like~sleepin',~specially~in~my~Molly's~chamber~\\
But~here~I~am~in~prison,~here~I~am~with~a~ball~and~chain~yeah~~\\


\textit{R:}\\
Musha~ring~dum~a~doo~dum~a~da~\\
Whack~for~my~daddy-o~\\
Whack~for~my~daddy-o~\\
There's~whiskey~in~the~jar-o~~\\


%
%----- New Song -----
\newpage\addcontentsline{toc}{section}{Líbám tě černou}
\section*{Líbám tě černou}
\index{Líbám tě černou}\typeout{Líbám tě černou}\index{BSP!Líbám tě černou}\textit{BSP}\\


Emi~G~Ami~C~2x\\


\gtxchord{Emi}{Líbám~tě~}\gtxchord{G}{černou,~}\gtxchord{Ami}{můru~}\gtxchord{C}{zlou,}\\
\gtxchord{Emi}{mým~světem~}\gtxchord{G}{kroužíš,~}\gtxchord{Ami}{hrou~jsi~}\gtxchord{C}{hrou,~ou~ou~}\gtxchord{G}{jéé.}\\
\gtxchord{}{Ústy~}\gtxchord{Ami}{ďábla~dítě,}\gtxchord{C}{~pýcha~}\gtxchord{D}{osloví~tě,}\\
\gtxchord{G}{zář~}\gtxchord{Ami}{tvou~je~maskou,~}\gtxchord{C}{hotel~}\gtxchord{D}{Underground.}\\


Líbám~tě~černou,~můru~zlou,\\
zády~se~točíš~za~duhou.\\
Ústy~ďábla~dítě,~pýcha~osloví~tě,\\
zář~zlou~je~maskou,~šeptáš,~hladíš,~křičíš~baby.\\


G~Ami~C~D~2x\\


\gtxchord{Emi}{Líbám~}\gtxchord{G}{černou,~}\gtxchord{Ami}{můru~}\gtxchord{C}{zlou,}\\
\gtxchord{Emi}{křídly~se~}\gtxchord{G}{točí~}\gtxchord{Ami}{za~du}\gtxchord{C}{hou,~jei~jei~}\gtxchord{G}{jéé.}\\
\gtxchord{}{Tvář~}\gtxchord{Ami}{ďábla~dítě,}\gtxchord{C}{~sám~}\gtxchord{D}{osloví~tě,}\\
\gtxchord{Emi}{Líbám~tě~}\gtxchord{G}{černou,~jé,~}\gtxchord{Ami}{můru~}\gtxchord{C}{zlou,}\\
\gtxchord{G}{Tvář~}\gtxchord{Ami}{ďábla~dítě,~}\gtxchord{C}{sám~teď~}\gtxchord{D}{osloví~tě,}\\
\gtxchord{G}{zář~}\gtxchord{Ami}{zlou~je~maskou,~}\gtxchord{C}{hotel~}\gtxchord{D}{Undergro}\gtxchord{Emi}{und~}\gtxchord{G}{jé}\gtxchord{Ami}{ééé~}\gtxchord{C}{ééé}\\


Emi~G~Ami~C~3x\\


Ústa~ďábla~dítě,~jé~láskou~osloví~tě,\\
zář~zlou~je~maskou,~kroužíš,~šeptáš,~křičíš~baby.\\


/~Z~křídel~pláč,~proč~dál~nehledáš,\\
~~hledáš~a~dál~to~nejde,~hledáš,~proklínáš~/\\


%
%----- New Song -----
\newpage\addcontentsline{toc}{section}{Telegraph road}
\section*{Telegraph road}
\index{Telegraph road}\typeout{Telegraph road}\index{Dire Straits!Telegraph road}\textit{Dire Straits}\\


\gtxchord{}{A~}\gtxchord{F}{long~time~ago~came~a~}\gtxchord{Dm}{man~on~a~track}\\
\gtxchord{C}{walking~thirty~miles~with~a~}\gtxchord{B$\flat$}{sack~on~his~back}\gtxchord{F}{}\\
\gtxchord{}{and~he~}\gtxchord{B$\flat$}{put~down~his~load~}\gtxchord{C}{where~he~}\gtxchord{F}{thought~it~was~the~best}\gtxchord{C7}{}\\
\gtxchord{B$\flat$}{he~made~a~home~in~the~wild}\gtxchord{Gm7}{erness}\gtxchord{B$\flat$}{}\\
\gtxchord{F}{he~built~a~}\gtxchord{Dm}{cabin~and~a~winter~store}\\
\gtxchord{}{and~he~}\gtxchord{C}{ploughed~up~the~ground~}\gtxchord{Am}{by~the~}\gtxchord{B$\flat$}{cold~lake~shore}\gtxchord{F}{}\\
\gtxchord{B$\flat$}{and~the~other~}\gtxchord{C}{travellers~came~}\gtxchord{F}{riding~down~the~}\gtxchord{C}{track}\\
\gtxchord{}{and~they~}\gtxchord{B$\flat$}{never~went~further~}\gtxchord{F/A}{and~they~}\gtxchord{Gm7}{never~went~back}\gtxchord{B$\flat$}{}\\
\gtxchord{F}{then~came~the~churches~}\gtxchord{Dm}{then~came~the~schools}\\
\gtxchord{C}{then~came~the~lawyers~}\gtxchord{B$\flat$}{then~came~the~rules}\gtxchord{F}{}\\
\gtxchord{B$\flat$}{then~came~the~}\gtxchord{Csus4}{trains~and~}\gtxchord{C}{the~}\gtxchord{F}{trucks~with~their~}\gtxchord{C}{loads}\\
\gtxchord{}{and~the~}\gtxchord{B$\flat$}{dirty~old~track}\gtxchord{B$\flat$}{~~~was~the~telegraph~road}\gtxchord{Dm}{}\\


\gtxchord{F}{Then~came~the~mines~-~}\gtxchord{Dm}{then~came~the~ore}\\
\gtxchord{C}{then~there~was~the~hard~times~}\gtxchord{B$\flat$}{then~there~was~}\gtxchord{B$\flat$}{a~~~}\gtxchord{F}{war}\\
\gtxchord{B$\flat$}{telegraph~sang~a~}\gtxchord{C}{song~a}\gtxchord{F}{bout~the~world~out}\gtxchord{C7}{side}\\
\gtxchord{B$\flat$}{telegraph~road~got~so~}\gtxchord{Gm7}{deep~and~so~wide}\\
\gtxchord{B$\flat$}{like~a~rolling~}\gtxchord{F}{river.~.~.}\\


\textit{solo}\\




\gtxchord{D}{~~~~~}\gtxchord{D7/F$\sharp$}{And~my~}\gtxchord{G}{radio~says~tonight~it's~gonna~freeze}\\
\gtxchord{Dm}{people~driving~home~from~the~factories}\\
\gtxchord{}{there's~}\gtxchord{C}{six~lanes~of~traffic}\\
\gtxchord{Am}{~~~~~three~lanes~moving~}\gtxchord{Dm}{slow.~.~.}\\


\textit{solo}\\




\gtxchord{C}{~~~I~used~to~}\gtxchord{F}{like~to~go~to~work~but~they~}\gtxchord{Dm}{shut~it~down}\\
\gtxchord{}{~~~I've~got~a~}\gtxchord{C}{right~to~go~to~work~but~there's~no~}\\
\hspace*\fill \gtxchord{B$\flat$}{work~here~to~be~found}\\
\gtxchord{}{~~~}\gtxchord{F}{yes~and~they~}\gtxchord{B$\flat$}{say~we're~gonna~have~}\gtxchord{C}{to~pay~}\gtxchord{F}{what's~owed}\gtxchord{C7}{}\\
\gtxchord{}{~~~we're~}\gtxchord{B$\flat$}{gonna~have~to~reap~from~}\gtxchord{Gm7}{seed~that's~been~sowed}\\
\gtxchord{B$\flat$}{~~~and~the~}\gtxchord{F}{birds~up~on~the~wires~and~the~}\gtxchord{Dm}{telegraph~poles}\\
\gtxchord{}{~~~they~can~}\gtxchord{C}{always~fly~away~from~this~rain~}\gtxchord{B$\flat$}{and~this~cold}\\
\gtxchord{}{~~~you~can~here~them~}\gtxchord{C7}{singing~out~their~}\gtxchord{F}{telegraph~code}\\
\gtxchord{}{~~~}\gtxchord{C}{all~the~w}\gtxchord{B$\flat$}{ay~down~the~telegraph~road}\gtxchord{Dm}{}\\




\textit{solo}\\




\gtxchord{C}{~~~You~know~I'd~}\gtxchord{F}{sooner~forget~but~I~re}\gtxchord{Dm}{member~those~nights}\\
\gtxchord{}{~~~when~}\gtxchord{C}{life~was~just~a~bet~on~a~race~}\gtxchord{B$\flat$}{between~the~lights}\\
\gtxchord{}{~~~}\gtxchord{F}{you~had~your~}\gtxchord{B$\flat$}{head~on~my~shoul}\gtxchord{C}{der~}\gtxchord{F}{you~had~your~}\gtxchord{C7}{hand~in~my~hair}\\
\gtxchord{}{~~~now~}\gtxchord{B$\flat$}{you~act~a~little~colder~like~you~}\gtxchord{Gm7}{don't~seem~to~care}\\
\gtxchord{B$\flat$}{~~~but~be}\gtxchord{F}{lieve~in~me~baby~and~I'll~}\gtxchord{Dm}{take~you~away}\\
\gtxchord{}{~~~from~}\gtxchord{C}{out~of~this~darkness~and~}\gtxchord{B$\flat$}{into~the~day}\\
\gtxchord{}{~~~from~these~rivers~of~}\gtxchord{C}{headlights~these~}\gtxchord{F}{rivers~of~rain}\gtxchord{C}{}\\
\gtxchord{F/A}{~~~from~the~}\gtxchord{B$\flat$}{anger~that~lives~on~}\gtxchord{C7}{the~}\gtxchord{F}{streets~with~these~}\gtxchord{C}{names}\\
\gtxchord{F/A}{~~~'cos~}\gtxchord{B$\flat$}{I've~run~every~red~light~}\gtxchord{C7}{on~}\gtxchord{F}{memory~lane}\gtxchord{F/A}{}\\
\gtxchord{}{~~~I've~}\gtxchord{B$\flat$}{seen~desperation~}\gtxchord{C7}{exp}\gtxchord{F}{lode~into~}\gtxchord{C}{flames}\gtxchord{F/A}{}\\
\gtxchord{B$\flat$}{~~~and~I~don't~}\gtxchord{C7}{want~to~}\gtxchord{F}{see~it~a}\gtxchord{C}{gain.~.~.}\\


\gtxchord{}{~~~From~}\gtxchord{Am}{all~of~these~signs~saying~}\gtxchord{Dm}{sorry~but~we're~closed}\\
\gtxchord{}{~~~all~the~}\gtxchord{B$\flat$}{way}\\


\textit{solo}\\

\addcontentsline{toc}{section}{God Rest Ye Merry Gentlemen}
\section*{God Rest Ye Merry Gentlemen}
\index{God Rest Ye Merry Gentlemen}

\gtxchord{}{God~}\gtxchord{Em}{rest~ye~merry,~}\gtxchord{Hm}{gentlemen,~}\\
\gtxchord{}{Let~}\gtxchord{A}{nothing~you~dis}\gtxchord{H}{may.}\\
\gtxchord{Em}{Remember~Christ~our~}\gtxchord{Hm}{Saviour}\\
\gtxchord{}{was~}\gtxchord{A}{born~on~Christmas}\gtxchord{H}{~day.}\\
\gtxchord{}{To~}\gtxchord{C}{save~us~all~from~}\gtxchord{G}{Satan's~powers}\\
\gtxchord{}{when~we~}\gtxchord{Hm}{were~gone~a}\gtxchord{D}{stray.}\\
\gtxchord{}{O,~}\gtxchord{G}{tidings~of~}\gtxchord{Hm}{comfort~and~}\gtxchord{Em}{joy,~comfort~and~}\gtxchord{D}{joy;}\\
\gtxchord{}{O,~}\gtxchord{G}{tidings~of~}\gtxchord{Hm}{comfort~}\gtxchord{D}{and~}\gtxchord{Em}{joy.}\\


In~Bethlehem,~in~Israel, this~blessed~Babe~was~born\\
And~laid~within~a~manger upon~this~blessed~morn\\
The~which~His~Mother~Mary did~nothing~take~in~scorn\\
O,~tidings~of~comfort~and~joy,~comfort~and~joy,\\
O,~tidings~of~comfort~and~joy.\\


From~God~our~Heavenly~Father a~blessed~Angel~came;\\
And~unto~certain~Shepherds brought~tidings~of~the~same:\\
How~that~in~Bethlehem~was~born the~Son~of~God~by~Name.\\
O,~tidings~of~comfort~and~joy,~comfort~and~joy,\\
O,~tidings~of~comfort~and~joy.\\

%
%----- New Song -----
\newpage\addcontentsline{toc}{section}{Země vzdálená}
\section*{Země vzdálená}
\index{Země vzdálená}\typeout{Země vzdálená}\index{BSP!Země vzdálená}\textit{BSP}\\


\gtxchord{A}{Smutnej~déšť~a~}\gtxchord{E}{město~v~kouři}, \gtxchord{Hmi}{ticho~prázdnejch~rán}\\
\gtxchord{F$\sharp$mi}{noční~můry~}\gtxchord{E}{pijou~silnej~čaj}\gtxchord{H}{}\\


\gtxchord{A}{Smutnej~déšť~}\gtxchord{E}{oči~mhouříš}, \gtxchord{Hmi}{už~v~nich~nejsem~sám}\\
\gtxchord{F$\sharp$mi}{ještě~málo~ži}\gtxchord{E}{jou~když~se~ptaj}\gtxchord{H}{}\\


\textit{Ref:}\\

\gtxchord{A}{Znám~tě~mnohem~}\gtxchord{E}{víc~země~vzdálená}\gtxchord{Hmi}{}\\
\gtxchord{F$\sharp$mi}{spát~s~tajem}\gtxchord{E}{nou~závratí}\gtxchord{H}{}\\


Roky~ztratí~sílu, když~ti~dál~šeptám:\\
"While~my~guitar~gently~weeps."\\


Pod~správnou~hvězdou v~malým~ráji~chtěl~jsem~říct:\\
"Stil~my~guitar~gently~weeps."\\

\gtxchord{G}{Den~chová~stín~v~}\gtxchord{D}{záclonách}\\
\gtxchord{A}{toulavejch~pár~}\gtxchord{E}{koček~strach}\\
\gtxchord{G}{sen~ti~skrývá~}\gtxchord{D}{na~víčkách}\\
\gtxchord{}{že~jsi~}\gtxchord{A}{mou}\\

\gtxchord{G}{Bláznům~se~jen~může~}\gtxchord{D}{smát}\\
\gtxchord{A}{když~nám~ráno~dává~}\gtxchord{E}{mat}\\
\gtxchord{G}{chtěl~jsem~dál~jen~}\gtxchord{D}{poslouchat}\\
\gtxchord{}{že~jsi~}\gtxchord{E}{má~že~jsi~má}\gtxchord{F$\sharp$}{}\\


\textit{Ref:2x}\\

\gtxchord{H}{Znám~tě~mnohem~}\gtxchord{F$\sharp$}{víc~země~}\gtxchord{C$\sharp$mi}{vzdálená}\\
\gtxchord{G$\sharp$mi}{spát~s~tajem}\gtxchord{F$\sharp$}{nou~závra}\gtxchord{C$\sharp$}{tí}\\
Jééééééé

\addcontentsline{toc}{section}{Biene Maja}
\section*{Biene Maja}
\index{Biene Maja}\index{Karel Gott!Biene Maja}\textit{Karel Gott}\\

\gtxchord{C}{In~einem~unbekannten~L}\gtxchord{G}{and,}\\
~vor~gar~nicht~allzu~langer~\gtxchord{C}{Zeit,~}\\
\gtxchord{}{war~eine~Biene~sehr~}\gtxchord{G}{bekannt,}\\
~von~der~sprach~alles~weit~und~\gtxchord{C}{breit.~}\\
\gtxchord{}{Und~}\gtxchord{C}{die}\gtxchord{G}{se~}\gtxchord{C}{Biene,~die~ich~meine,~nennt~sich~}\gtxchord{G}{Maja,~}\\
\gtxchord{}{kleine,~freche,~schlaue~Biene~}\gtxchord{C}{Maja.~}\\
\gtxchord{}{Maja~fliegt~durch~ihre~}\gtxchord{G}{Welt,~zeigt~uns~das,~was~ihr~ge}\gtxchord{C}{fällt.~}\\
\gtxchord{}{Wir~treffen~heute~unsre~Freundin,~Biene~}\gtxchord{G}{Maja,~}\\
\gtxchord{}{diese~kleine,~freche~Biene~}\gtxchord{C}{Maja.~}\\
\gtxchord{C7}{Maja,~alle~lieben~}\gtxchord{F}{Maja~!~~}\\
\gtxchord{C}{Maja!~(Maja!)~Maja!~(Maja!)~Maja~!~Erzäh}\gtxchord{G}{le~uns~von~}\gtxchord{C}{dir~!~}\\

Wenn~ich~an~einem~schönen~Tag\\
durch~eine~Blumenwiese~geh,~\\
und~kleine~Bienen~fliegen~seh,\\
denk~ich~an~eine,~die~ich~mag.~\\
Und~diese~Biene,~die~ich~meine,~nennt~sich~Maja,~\\
kleine,~freche,~schlaue~Biene~Maja.~\\
Maja~fliegt~durch~ihre~Welt,~zeigt~uns~das,~was~ihr~gefällt.~\\
Wir~treffen~heute~unsre~Freundin,~Biene~Maja,~\\
diese~kleine,~freche~Biene~Maja.~\\
Maja,~alle~lieben~Maja~!~~\\
Maja!~(Maja!)~Maja!~(Maja!)~Maja~!~Erzähle~uns~von~dir~!

\addcontentsline{toc}{section}{Ducktales}
\section*{Ducktales}
\index{Ducktales}

\gtxchord{E}{Life~is~like~a~hurricane}\\
\gtxchord{D}{here~in~}\gtxchord{A}{Duckburg.}\\
\gtxchord{E}{Race~cars,~lasers,~aeroplanes,}\\
\gtxchord{D}{it's~}\gtxchord{A}{~A~}\gtxchord{D}{~duck-~}\gtxchord{A}{blur.}\\
\gtxchord{F$\sharp$5}{Might~solve~A~}\gtxchord{B}{~mystery,}\\
\gtxchord{A}{Or~rewrite~}\gtxchord{B}{~history~--}\\

\textit{chorus:}\\

\gtxchord{E}{DuckTales~(oooh~ooooh)!}\\
\gtxchord{C}{Every~day~they're~}\gtxchord{D}{~out~there~making}\\
\gtxchord{E}{DuckTales~(oooh~ooooh)!}\\
\gtxchord{C}{Tales~of~daring~}\gtxchord{D}{~do~bad~and~good}\\
\gtxchord{E}{Luck~tales~(oooh~ooooh)!}\\

textit{bridge:}\\

\gtxchord{C$\sharp$'5}{~D-D-D-Danger!~}\gtxchord{B}{~Watch~behind~you,}\\
\gtxchord{A}{There's~a~stranger~}\gtxchord{E}{~out~to~find~you}\\
\gtxchord{D}{What~to~do?~Just~}\gtxchord{A}{~grab~on~to~some~--}\\

\textit{chorus:}\\
DuckTales~(oooh~ooooh)!\\
Every~day~they're~out~there~making\\
DuckTales~(oooh~ooooh)!\\
Tales~of~daring~do~bad~and~good\\
Luck~tales~(oooh~ooooh)!

%----- New Song -----
\newpage\addcontentsline{toc}{section}{'74-'75}
\begin{center}\section*{'74-'75}\end{center}
\index{'74-'75}\index{The Connells!'74-'75}\begin{center}\textit{The Connells}\end{center}

\textit{Intro:}\\
\begin{gtxtab}
\footnotesize \verb!|----------0--3------0-0-0-|! \normalsize \newline
\footnotesize \verb!|----------1--0------1-0-1-|! \normalsize \newline
\footnotesize \verb!|----------0--0------2-2-2-|! \normalsize \newline
\footnotesize \verb!|--2-0-----2--0--2-2-2-2-2-|! \normalsize \newline
\footnotesize \verb!|-0----3-0-3--2--0-0-0-0-0-|! \normalsize \newline
\footnotesize \verb!|-------------3------------|! \normalsize \newline
\end{gtxtab}

\textit{1.}\\ \\
\gtxchord{F}{Got~no~}\gtxchord{C}{reason~for~}\gtxchord{F}{coming~to~me~and~the~}\gtxchord{C}{rain~}\gtxchord{G}{running~}\gtxchord{F}{down~}\\
{there's~no~}\gtxchord{C}{reason}\gtxchord{Am}{}\gtxchord{A2}{}\\
\gtxchord{F}{and~the~}\gtxchord{C}{same~voice~}\gtxchord{F}{coming~to~me~like~it's~}\gtxchord{C}{all~}\gtxchord{G}{slowing~}\gtxchord{F}{down~}\\
{and~}\gtxchord{C}{believe~me}\gtxchord{G}{}\\

\textit{R1:}\\
{I~was~the~}\gtxchord{Am}{one~who~let~you~}\gtxchord{C}{know,~}\\
{I~was~just~}\gtxchord{G}{sorry~ever~}\gtxchord{F}{after}\\
{seventy-}\gtxchord{Am}{four~,~seventy-}\gtxchord{C}{five}\gtxchord{G}{}\\

\textit{2.}\\
{It's~not~easy,~nothing~to~say~'cause~it's~already~said~}\\
{It's~never~easy}\\
{When~I~look~on~your~eyes~then~I~find~that~I'll~do~fine~}\\
{When~I~look~on~your~eyes~then~I~do~better}\\

\textit{R2:}\\
{I~was~the~one~who~let~you~know,~}\\
{I~was~just~sorry~ever~after}\\
{seventy-four~,~seventy-five}\\
{Givin~me~more~and~I'll~defy,~}\\
{cause~you're~really~only~after}\\
{seventy-four~,~seventy-five}\\

\textit{Repeat Intro}\\
\textit{Solo~(R)}\\

\textit{3.}\\
{Got~no~reason~for~coming~to~me~and~the~rain~running~down~}\\
{there's~no~reason}\\
{When~I~look~on~your~eyes~then~I~find~that~I'll~do~fine~}\\
{When~I~look~on~your~eyes~then~I~do~better}\\

\textit{R2~2x}\\
\textit{Solo~(R)}\\
\vfill
%----- New Song -----
\addcontentsline{toc}{section}{I Will Survive}
\begin{center} \section*{I Will Survive}\end{center}
\index{I Will Survive}\index{Gloria Gaynor!I Will Survive}\begin{center}\textit{Gloria Gaynor}\end{center}

\gtxchord{Am}{}\gtxchord{Dm}{}\gtxchord{G}{}\gtxchord{C}{}\gtxchord{F}{}\gtxchord{Bm}{}\gtxchord{Em}{}\gtxchord{E}{}\\

\textit{1.}\\
{At~}\gtxchord{Am}{first~I~was~afraid,~I~was~}\gtxchord{Dm}{petrified~}\\
{I~kept~thinkin'~}\gtxchord{G}{I~could~never~live~without~you~}\gtxchord{C}{by~my~side~}\\
{But~then~I~}\gtxchord{F}{spent~so~many~nights~just~thinking~}\\
\hspace*\fill \gtxchord{Bm}{how~you’ve~done~me~wrong~}\\
{And~I~grew~}\gtxchord{Em}{strong,~I~learned~}\gtxchord{E}{how~to~get~along...}\\

\textit{2.}\\
{And~so~you're~back~from~outer~space,~}\\
{I~just~walked~in~to~find~you~here~with~that,}\\
\hspace*\fill {that~look~upon~your~face,~~}\\
{I~should~have~changed~that~stupid~lock,}\\
\hspace*\fill {I~should~have~made~you~leave~your~key~-~}\\
{If~I’d~have~known~for~just~one~second}\\
\hspace*\fill {you'd~be~back~to~bother~me.~}\\

\textit{3.}\\
{Oh~now~go,~walk~out~the~door,~}\\
{Just~turn~around~now,~cause~you're~not~welcome~anymore.~}\\
{Weren't~you~the~one~who~tried~to~hurt~me~with~good-bye?~}\\
{Did~you~think~I'd~crumble?}\\
\hspace*\fill {Did~you~think~I'd~lay~down~and~die?}\\

\textit{4.}\\
{Oh~not~I,~I~will~survive,~}\\
{Yeah,~as~long~as~I~know~how~to~love,~I~know~I'll~be~alive.~}\\
{I've~got~all~my~life~to~live,~I've~got~all~my~love~to~give,~}\\
{I~will~survive,~I~will~survive,~Yeah,~yeah...}\\

\textit{Solo}\\

\textit{5.}\\
{It~took~all~the~strength~I~had~just~not~to~fall~apart,~~}\\
{I’m~tryin'~hard~to~mend~the~pieces~of~my~broken~heart,~}\\
{And~I~spent~oh~so~many~nights~just~feelin'~sorry~for~myself,~}\\
{I~used~to~cry,~But~now~I~hold~my~head~up~high.~}\\

\textit{6.}\\
{And~you’ll~see~me~with~somebody~new,~}\\
{I'm~not~that~stupid~little~person~still~in~love~with~you.~}\\
{And~so~you~thought~you’d~just~drop~by}\\
\hspace*\fill {and~you~expect~me~to~be~free,~}\\
{But~now~I'm~saving~all~my~lovin'}\\
\hspace*\fill {for~someone~who's~lovin'~me.}\\

\textit{7. = 3.}\\

\textit{8. = 4.}\\

\textit{9. = 3.}\\

\textit{8. = 4. (and fade)}\\

%----- New Song -----
\newpage\addcontentsline{toc}{section}{It's My Life}
\begin{center} \section*{It's My Life}\end{center}
\index{It's My Life}\index{Bon Jovi!It's My Life}\begin{center}\it Bon Jovi\end{center}

\textit{Intro}\\
\begin{gtxtab}
\footnotesize \verb!E|--------------1-0---------------------|! \normalsize \newline
\footnotesize \verb!B|----1-------5-----1--1----1--0--------| ! \normalsize \newline
\footnotesize \verb!G|*---2-----5----------2----------2----*|! \normalsize \newline
\footnotesize \verb!D|*---2--/7------------3---------------*|! \normalsize \newline
\footnotesize \verb!A|--------------------------------------| ! \normalsize \newline
\footnotesize \verb!E|--------------------------------------|! \normalsize \newline
\end{gtxtab}

\textit{1.}\\ \\
\gtxchord{Am}{This~ain't~a~song~for~the~}\gtxchord{Em}{broken~hearted}\gtxchord{G}{}\\
{Nor~a~}\gtxchord{Am}{silent~prayer~for~}\gtxchord{Em}{death-departed}\gtxchord{G}{}\\
{I~a}\gtxchord{Am}{in't~gonna~be~just~a~}\gtxchord{Em}{face~in~the~crowd}\\
{You're~gonna~}\gtxchord{C}{hear~my~voice~when~I~}\gtxchord{G}{shout~it~out~}\gtxchord{Am}{loud}\\

\textit{Chorus:}\\ \\
{It's~my~}\gtxchord{Am}{life,~it's~}\gtxchord{F}{now~or~never}\gtxchord{C}{}\\
{I~ain't~gonna~}\gtxchord{G}{live~forever}\gtxchord{Am}{}\\
{I~just~want~to~}\gtxchord{F}{live~when~I'm~a}\gtxchord{C}{live}\gtxchord{Em}{}\gtxchord{G}{}\\
{It's~my~}\gtxchord{Am}{life;~my~heart~is~like~an~}\gtxchord{F}{open~highway}\gtxchord{C}{}\\
{Like~Frankie~said~I~did~it~}\gtxchord{G}{my~way,}\gtxchord{Am}{}\\
{I~just~wanna~}\gtxchord{F}{live~when~I'm~a}\gtxchord{Em}{live}\\
\gtxchord{Em}{It's~}\gtxchord{G}{my~l}\gtxchord{C}{ife}\\

\textit{2.}\\
{This~is~for~ones~who~stood~their~ground}\\
{Like~Tommy~and~Gina,~never~backed~down}\\
{Tomorrow's~getting~harder~make~no~mistake}\\
{Luck~ain't~even~lucky~got~to~make~your~own~breaks}\\

\textit{Chorus}\\

\textit{Solo}\\

\textit{Bridge:}\\ \\
{You~be}\gtxchord{G}{tter~stand~tall~when~they're~}\gtxchord{C}{calling~you~out}\\
{Don't~b}\gtxchord{Am}{end~don't~break~baby~}\gtxchord{Em}{don't~back~down}\gtxchord{G}{~}\\

\textit{Chorus 2x}
%----- New Song -----
\addcontentsline{toc}{section}{My Name Is Luka}
\begin{center} \section*{My Name Is Luka}\end{center}
\index{My Name Is Luka}\index{Suzanne Vega!My Name Is Luka}\begin{center}\it Suzanne Vega\end{center}

\textit{Intro }\\ \\
\gtxchord{/:~G~D~C~D~:/}{}

\textit{1.}\\ \\
\gtxchord{G}{~~My~name~is~}\gtxchord{D}{Luka}\\
\gtxchord{C}{~~I~live~on~the~}\gtxchord{D}{second~floor}\\
\gtxchord{G}{~~I~live~upstairs~}\gtxchord{D}{from~you}\\
\gtxchord{C}{~~Yes~I~think~you've~}\gtxchord{D}{seen~me~before~}\\

\textit{Chorus 1:}\\ \\
\gtxchord{Em}{~~If~you~hear~}\gtxchord{D}{something~late~at~night}\\
\gtxchord{Em}{~~Some~kind~of~}\gtxchord{D}{trouble.~Some~kind~of~fight}\\
\gtxchord{C}{~~Just~don't~}\gtxchord{D}{ask~me~what~it~was}\\
\gtxchord{C}{~~Just~don't~}\gtxchord{D}{ask~me~what~it~was}\\
\gtxchord{C}{~~Just~don't~}\gtxchord{D}{ask~me~what~it~was~}\\

\textit{2. }\\
{I~think~it's~because~I'm~clumsy}\\
{I~try~not~to~talk~too~loud}\\
{Maybe~it's~because~I'm~crazy}\\
{I~try~not~to~act~too~proud}\\

\textit{Chorus 2:}\\
{They~only~hit~until~you~cry}\\
{and~after~that~you~don't~ask~why}\\
{you~just~don't~argue~anymore}\\
{you~just~don't~argue~anymore}\\
{you~just~don't~argue~anymore}\\

\textit{Solo~(intro)}\\

\textit{3.}\\
{Yes~I~think~I'm~okay}\\
{I~walked~into~the~door~again}\\
{Well,~if~you~ask~that's~what~I'll~say}\\
{and~it's~not~your~business~anyway}\\

\textit{Chorus 3:}\\
{I~guess~I'd~like~to~be~alone}\\
{with~nothing~broken,~nothing~thrown~}\\
{Just~don't~ask~me~how~I~am}\\
{Just~don't~ask~me~how~I~am}\\
{Just~don't~ask~me~how~I~am}\\


\textit{4. }\\
{My~name~is~Luka}\\
{I~live~on~the~second~floor}\\
{I~live~upstairs~from~you}\\
{Yes~I~think~you've~seen~me~before~}\\


\textit{Chorus 1}\\


\textit{Chorus 2}\\


\textit{Solo (intro)}

%----- New Song -----
\newpage\addcontentsline{toc}{section}{Underneath Your Clothes}
\begin{center} \section*{Underneath Your Clothes}\end{center}
\index{Underneath Your Clothes}\index{Shakira!Underneath Your Clothes}\begin{center}\it Shakira\end{center}

\textit{1.}\\ \\
\gtxchord{Fm}{You're~a~}\gtxchord{Cm}{song~}\gtxchord{C$\sharp$}{written~by~the~}\gtxchord{E$\flat$}{hands~of~G}\gtxchord{Fm}{od}\\
{Don't~get~me~wr}\gtxchord{Cm}{ong}\\
{'cause~th}\gtxchord{C$\sharp$}{is~might~sound~to~yo}\gtxchord{E$\flat$}{u~a~bit~o}\gtxchord{Fm}{dd}\\
{But~you~o}\gtxchord{Cm}{wn~the~p}\gtxchord{C$\sharp$}{lace}\\
{where~}\gtxchord{E$\flat$}{all~my~thoughts~go}\gtxchord{Fm}{~hidi}\gtxchord{Cm}{ng}\\
{And~r}\gtxchord{C$\sharp$}{ight~under~your~clothes~is~wh}\gtxchord{E$\flat$}{ere~I'll~find~them}\\

\textit{Chorus:}\\ \\
\gtxchord{A$\flat$}{Undern}\gtxchord{Cm7}{eath~your~c}\gtxchord{C$\sharp$}{lothes,~there's~an~}\gtxchord{E$\flat$}{endless~story}\\
\gtxchord{A$\flat$}{There's~the~m}\gtxchord{Cm7}{an~I~c}\gtxchord{C$\sharp$}{hose,~there's~my~}\gtxchord{E$\flat$}{territory}\\
{And~}\gtxchord{Cm}{all~the~things~I~des}\gtxchord{Fm}{erve}\\
{For~b}\gtxchord{C$\sharp$}{eing~such~a~g}\gtxchord{E$\flat$}{ood~girl,~honey}\gtxchord{A$\flat$}{}\gtxchord{C$\sharp$}{}\\

\textit{2.}\\
{'Cause~of~you~I~forgot~the~smart~ways~to~lie}\\
{Because~of~you~}\\
{I'm~running~out~of~reasons~to~cry}\\
{When~the~friends~are~gone}\\
{When~the~party~is~over}\\
{We~will~still~belong~to~each~other}\\

\textit{Chorus}\\

\textit{Coda:}\\
{I~}\gtxchord{B}{love~you~more}\gtxchord{B/Ab}{~than~all~tha}\gtxchord{A$\flat$m}{t's~on~the~planet}\\
{moving,~talking,~walking,~br}\gtxchord{F$\sharp$}{eathing}\\
{You~kn}\gtxchord{E}{ow~it's~true,~oh~babe~it's~so~funny}\\
{You~}\gtxchord{F$\sharp$}{almost~don't~believe~it}\\

{As~every~voice~is~hanging~from~the~silence}\\
{Lamps~are~hanging~from~the~ceiling}\\
{Like~a~lady~tied~to~her~manners}\\ \\
\gtxchord{F$\sharp$}{I'm~tied~up~to~this~f}\gtxchord{Fm}{eel(ing)}\\

\textit{Solo:}\\ \\
\gtxchord{:~Fm~Cm~C$\sharp$~Eb~:}{~(3x)}\\

\textit{Chorus 2x}\\
{For~being~such~a~good~girl~...}\\
\vfill
\addcontentsline{toc}{section}{Roxanne}
\begin{center} \section*{Roxanne}\end{center}
\index{Roxanne}\index{Sting!Roxanne}\begin{center}\it Sting\end{center}

\textit{Intro:}\\ \\
\gtxchord{|~Gm7~~|~Gm7~Dm7/F~|~Ebmaj7~Dm7~|~Cm7~Fsus4~|~Gsus4}{}

\textit{1.}\\ \\
{Ro}\gtxchord{Gm7}{xanne}\gtxchord{Dm7/F}{,~you~don't~have~to~}\gtxchord{E$\flat$maj7}{put~on~the~red~light}\gtxchord{Dm7}{}\\
\gtxchord{Cm7}{~~~Those~days~are~ove}\gtxchord{Fsus4}{r,~you~don't~have~to~}\\\hspace*\fill\gtxchord{Gsus4}{sell~your~body~to~the~night}\\
{Roxanne,~you~don't~have~to~wear~that~dress~tonight~}\\
Walk~the~streets~for~money,\\\hspace*\fill~you~don't~care~if~it's~wrong~or~if~it's~right\\

\textit{Chorus:}\\ \\
{Ro}\gtxchord{Cm7}{xanne}\gtxchord{Fsus4}{,~you~don't~have~to~}\gtxchord{Gsus4}{put~on~the~red~light~}\\
Roxanne,~you~don't~have~to~put~on~the~red~light~\\

\gtxchord{Cm}{Roxan}\gtxchord{B$\flat$}{ne~(Put~on~the~red~light)~}\\
\gtxchord{E$\flat$}{Roxan}\gtxchord{F}{ne~(Put~on~the~red~light)~}\\
\gtxchord{F}{Roxan}\gtxchord{Gm}{ne~(Put~on~the~red~light)~}\\
\gtxchord{Cm}{Roxan}\gtxchord{B$\flat$}{ne~(Put~on~the~red~light)~}\\
\gtxchord{E$\flat$}{Roxan}\gtxchord{F}{ne~(Put~on~the~red~light)~~}\gtxchord{Gsus4}{oh~}\\

\textit{2.}\\
{I~loved~you~since~I~knew~ya,~I~wouldn't~talk~down~to~ya~}\\
I~have~to~tell~you~just~how~I~feel,\\\hspace*\fill~I~won't~share~you~with~another~boy~\\
{I~know~my~mind~is~made~up,~so~put~away~your~make~up~}\\
{Told~you~once~I~won't~tell~you~again~it's~a~crime~way~}\\

\textit{Chorus}

\newpage\addcontentsline{toc}{section}{Englishman in New York}
\begin{center} \section*{Englishman in New York}\end{center}
\index{Englishman in New York}\index{ Sting!Englishman in New York}\begin{center}\it Sting\end{center}

\gtxchord{Bm}{~~}\gtxchord{Bm7}{~}\\
\textit{1.}\\ \\
\gtxchord{Em}{I~don't~drink~c}\gtxchord{A}{offee~I~take~}\gtxchord{Bm}{tea~my~dear}\gtxchord{Bm7}{~}\\
\gtxchord{Em}{I~like~my~t}\gtxchord{A}{oast~done~on~the~}\gtxchord{Bm}{side}\gtxchord{Bm7}{~}\\
\gtxchord{Em}{And~you~can~h}\gtxchord{A}{ear~it~in~my~}\gtxchord{Bm}{accent~when~I~}\gtxchord{Bm7}{talk~}\\
{I'm~an~E}\gtxchord{Em}{nglishman~}\gtxchord{A}{in~New~Y}\gtxchord{Bm}{ork}\gtxchord{Bm7}{~}

\textit{2.}\\
{See~me~walking~down~Fifth~Avenue~}\\
{A~walking~cane~here~at~my~side~}\\
{I~take~it~everywhere~I~walk~}\\
{I'm~an~Englishman~in~New~York~}

\medskip\textit{Chorus:}\\ \\
\gtxchord{Em}{I'm~an~a}\gtxchord{A}{lien~~~}\gtxchord{Bm}{I'm~a~legal~}\gtxchord{Bm7}{alien~}\\
{I'm~an~E}\gtxchord{Em}{nglishman~}\gtxchord{A}{in~New~Y}\gtxchord{Bm}{ork}\gtxchord{Bm7}{~}\\
\gtxchord{Em}{I'm~an~a}\gtxchord{A}{lien~~~}\gtxchord{Bm}{I'm~a~legal~}\gtxchord{Bm7}{alien~}\\
{I'm~an~E}\gtxchord{Em}{nglishman~}\gtxchord{A}{in~New~Y}\gtxchord{Bm}{ork}\gtxchord{Bm7}{~}

\textit{3.}\\
{If~``manners~maketh~man''~as~someone~said~}\\
{Then~he's~the~hero~of~the~day~}\\
{It~takes~a~man~to~suffer~ignorance~and~smile~}\\
{Be~yourself~no~matter~what~they~say~}

\medskip\textit{Chorus}

\textit{Bridge:}\\ \\
\gtxchord{D}{Modesty,~propriety~can~l}\gtxchord{A}{ead~to~not}\gtxchord{A7}{oriety~}\\
\gtxchord{Bm}{You~could~end}\gtxchord{Bm7}{~up~as~the~only~}\gtxchord{F$\sharp$}{one~}\\
{G}\gtxchord{G}{entleness,~sobriety~are~r}\gtxchord{A}{are~in~this~society~}\\
{At~}\gtxchord{Gdim7}{night~a~candle's~brighter~than~the~}\gtxchord{Bm}{sun~}

\textit{4.}\\
{Takes~more~than~combat~gear~to~make~a~man~}\\
{Takes~more~than~license~for~a~gun~}\\
{Confront~your~enemies,~avoid~them~when~you~can~}\\
{A~gentleman~will~walk~but~never~run~}

\medskip\textit{5. = 3., Chorus}
\addcontentsline{toc}{section}{Sixteen Tons}
\begin{center} \section*{Sixteen Tons}\end{center}
\index{Sixteen Tons}\index{Tennessee Ernie Ford!Sixteen Tons}\begin{center}\it Tennessee Ernie Ford\end{center}

\textit{1.}\\ \\
\gtxchord{Am}{Some~people~say~a~man's~}\gtxchord{Dm}{made~out~of~}\gtxchord{E}{mud}\\
{but~a~}\gtxchord{Am}{poor~man's~made~out~of~}\gtxchord{Dm}{muscle~and~}\gtxchord{E}{blood}\\
\gtxchord{Am}{Muscle~and~blood,~}\gtxchord{Dm}{skin~and~bones,}\\
\gtxchord{Am}{a~mind~that's~weak~and~a~}\gtxchord{E}{body~that's~}\gtxchord{E7}{strong}

\textit{Chorus:}\\
{You~load~}\gtxchord{Am}{sixteen~}\gtxchord{Am/G}{tons~and~}\gtxchord{Am/F}{whaddya~}\gtxchord{E}{get,}\\
{a}\gtxchord{Am}{nother~day~}\gtxchord{Am/G}{older~and~}\gtxchord{Am/F}{deeper~in~}\gtxchord{E}{debt}\\
{Saint~}\gtxchord{Am}{Peter~don't~you~call~me~'cause~}\gtxchord{Dm}{I~can't~go,}\\
{I}\gtxchord{Am}{~owe~my~soul~to~the~}\gtxchord{E}{company~}\gtxchord{Am}{store}

\textit{2.}\\
{I~was~born~one~morning~when~the~sun~didn't~shine,}\\
{picked~up~my~shovel~and~walked~to~the~mine}\\
{I~loaded~sixteen~tons~of~number~nine~coal;}\\
the~straw~boss~said~``well,~damn~my~soul.''

\medskip\textit{Chorus}

\textit{3.}\\
{I~was~born~one~morning,~it~was~drizzling~rain.}\\
{Fightin'~and~trouble~are~my~middle~name.}\\
{I~was~raised~in~a~cane~break~by~an~old~mama~lion,}\\
{can't~no~high-toned~woman~make~me~walk~the~line}

\medskip\textit{Chorus}

\textit{4.}\\
{If~you~see~me~comin'~you~better~step~aside;}\\
{another~man~didn't~and~another~man~died.}\\
{I've~got~a~fist~full~of~iron~and~a~fist~full~of~steel,}\\
{if~the~left~one~don't~get~you,~well,~the~right~one~will}

\textit{Chorus}
\addcontentsline{toc}{section}{All By Myself}
\begin{center} \section*{All By Myself}\end{center}
\index{All By Myself}\index{Eric Carmen!All By Myself}\begin{center}\it Eric Carmen\end{center}
\textit{Intro:} \textbf{\scriptsize F} 8x

\textit{1.}\\ \\
\gtxchord{F}{When~I~was~young,~}{I~never~}\gtxchord{B$\flat$m/F}{needed~anyone}\gtxchord{F~Am7-5/Eb}{}\\
{And~makin'~}\gtxchord{Dsus4}{love~was~}\gtxchord{D}{just~for~fun}\gtxchord{Gm}{...}\gtxchord{B$\flat$m6}{those~days~are~gone}

\medskip\textit{Bridge 1:} \textbf{\scriptsize F/A~F/A~Gm7-5~C/E}

\textit{2.}\\
{Livin'~alone,~I~think~of~all~the~friends~I've~known}\\
{But~when~I~dial~the~telephone, nobody's~home}

\medskip\textit{Bridge 2:} \textbf{\scriptsize F/A F/A D7 D G7 C7 C7}

\textit{Chorus:}\\ \\
\gtxchord{F}{All~by~mys}\gtxchord{Am}{elf}{,~don't~wanna~be}\gtxchord{Am7-5/Eb}{}\\
{All~by~}\gtxchord{D7}{myself}\gtxchord{Gm}{~anymore}\gtxchord{Gm7-5/C$\sharp$~~C7}{}\\
\gtxchord{F}{All~by~mys}\gtxchord{Am}{elf}{,~don't~wanna~live}\gtxchord{Am7-5/Eb}{}\\
{All~by~}\gtxchord{D7}{myself}\gtxchord{Gm}{~anymore}\gtxchord{Gm7-5/C$\sharp$~~C7}{}

\textit{3.}\\
{Hard~to~be~sure,~sometimes~I~feel~so~insecure}\\
{And~love,~so~distant~and~obscure,~remains~the~cure}\\

\textit{Bridge 1, 4. = 1., Bridge 2, Chorus}

%%%%%%
% INDEX
%%%%%%

\newpage
\fancypagestyle{plain}{%
  \fancyhf{}                          % clear all header and footer fields
  \renewcommand{\headrulewidth}{0pt}
  \renewcommand{\footrulewidth}{0pt}
}
\small\printindex
\end{document}
