\begin{song}{What Becomes of the Broken Hearted}{Jimmy Ruffin}

\vspace{-0.7cm}
\songpart{1.  }
\begin{guitar}
^ [A] As I walk this land of [C#m]broken dreams, \\
^ [F#m]  I have visions of [D]many [E]things. \\
^ [A] But happiness is [C#m]just an illusion, \\
^ [F#m] filled with sadness [D]and con[E]fusion. \\
\end{guitar}

\songpart{Chorus:}
\begin{guitar}
^ [B] What becomes of the [D#m]broken-hearted, \\
^ [G#m] who has love that's [E]now departed? \\
^ [B]I know I've got to find [D#m]some kind of peace of mind, \\
^ [D#]maybe...[E]\\
\end{guitar}

\songpart{2.   }
\begin{guitar}
The roots of love grow all around, \\
but for me they come a tumbling down. \\
Every day heartaches grow a little stronger, \\
I can't stand this pain much longer. \\
\end{guitar}

\songpart{3.   }
\begin{guitar}
I walk in shadows searching for light, \\
cold and alone no comfort in sight. \\
Hoping and praying for someone who cares, \\
always moving and going nowhere.\\
\end{guitar}

\songpart{Chorus}

\songpart{4.   }
\begin{guitar}
I'm searching though I don't succeed, \\
for someone's love there's a growing need. \\
All is lost there's no place for beginning, \\
all that's left is an unhappy ending. \\
\end{guitar}

\songpart{Outro (fade out):}
\begin{guitar}
^ [A] What becomes of the [C#m]broken-hearted,\\
^ [F#m] who has love that's [D]now de[E]parted?\\
I know I've got to find some kind of peace of mind \\
I'll be searching everywhere, just to find someone to care, \\
I'll be looking every day, I know I'm gonna find a way. \\
Nothing's going to stop me now... I'll find a way somehow. \\
I'll be looking every day, I know I'm gonna find a way...\\
\end{guitar}

\end{song}
